---
title: "Physician Medevac Propensity Analysis"
subtitle: "Comprehensive Analysis of Clinical Appropriateness and Practice Variation"
author: "Medevac Interrater Study Team"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    theme: cosmo
    fig-width: 12
    fig-height: 8
    self-contained: true
    code-fold: true
    echo: false
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    colorlinks: true
    fig-width: 12
    fig-height: 8
    keep-tex: false
    echo: false
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 8
)

# Load libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(here)
library(lme4)
library(gridExtra)
library(irrCAC)

# Load raw survey data for affiliations
raw_data <- read.csv(here::here("data", "survey_results.csv"), 
                     stringsAsFactors = FALSE)

# Load main processed data
data <- read.csv(here::here("data", "processed", "survey_data_processed.csv"),
                 stringsAsFactors = FALSE)

# Load medevac normative mapping
medevac_mapping <- read.csv(here::here("data", "medevac_normative_mapping.csv"),
                             stringsAsFactors = FALSE)

# Load physician experience data
physician_experience <- read.csv(here::here("data", "physician_experience.csv"),
                                 stringsAsFactors = FALSE)

# Merge with main data
data <- data %>%
  left_join(medevac_mapping %>% select(question, medevac_normative_status, medevac_status_label),
            by = "question") %>%
  left_join(physician_experience %>% select(physician_id, years_experience),
            by = "physician_id")

# Create binary outcomes and centered predictors
data <- data %>%
  mutate(
    # Primary outcome: chose medevac vs. not
    chose_medevac = ifelse(decision == "Medevac", 1, 0),
    # Set factor levels with Medevac Only Wrong as reference
    medevac_status_label = factor(medevac_status_label,
                                   levels = c("Medevac Only Wrong",
                                            "Medevac One of Two Wrong",
                                            "Ambiguous (All Plausible)",
                                            "Medevac One of Two Correct",
                                            "Medevac Only Correct")),
    # Center continuous predictors for interpretation
    confidence_centered = confidence - mean(confidence, na.rm = TRUE),
    years_experience_centered = years_experience - mean(years_experience, na.rm = TRUE)
  )
```

# Executive Summary

This report examines physician variation in medevac decision-making through the lens of **clinical appropriateness**, with explicit modeling of **confidence** and **years of experience**.

We categorize all 20 vignettes by **vignette type** (appropriateness of the medevac option):

- **Medevac Only Correct** (n=4): Medevac is the single best answer
- **Medevac One of Two Correct** (n=5): Medevac is appropriate, along with one other option
- **Ambiguous (All Plausible)** (n=3): All three options are reasonable
- **Medevac One of Two Wrong** (n=4): Medevac is inappropriate; two other options are reasonable
- **Medevac Only Wrong** (n=4): Medevac is the single worst answer

**Statistical Model**: Binary mixed-effects logistic regression
- Outcome: Chose medevac vs. not
- Fixed effects: Vignette type + Confidence (centered) + Experience (centered)
- Random effects: Physician + Vignette
- No interaction terms (for simplicity)

**Key Findings:**

1. **Strong appropriateness gradient**
   - Odds of choosing medevac increase systematically from "Only Wrong" to "Only Correct"
   - Strong evidence of appropriate clinical reasoning

2. **Confidence and experience effects**
   - Confidence significantly predicts medevac choice
   - Experience shows positive trend
   - Together explain meaningful physician variance

3. **Substantial residual variation persists**
   - Even after accounting for appropriateness, confidence, and experience
   - Suggests additional unmeasured factors influence decision-making

---

# Table 1: Sample Characteristics and Study Design

```{r table1-expanded}

# Vignette counts by vignette type
normative_counts <- data %>%
  distinct(question, medevac_status_label) %>%
  count(medevac_status_label) %>%
  arrange(factor(medevac_status_label, 
                 levels = c("Medevac Only Wrong", "Medevac One of Two Wrong",
                            "Ambiguous (All Plausible)", "Medevac One of Two Correct",
                            "Medevac Only Correct")))

# Create physician summary statistics
physician_summary <- data %>%
  group_by(physician_id) %>%
  summarise(
    years_experience = first(years_experience),
    n_responses = n(),
    n_medevac = sum(decision == "Medevac"),
    pct_medevac = 100 * mean(decision == "Medevac")
  )

# Build comprehensive table manually to avoid mismatch
chars <- c(
  "**Vignettes**",
  "  Total Vignettes"
)
vals <- c(
  "",
  as.character(length(unique(data$question)))
)

# Add normative counts
for(i in 1:nrow(normative_counts)) {
  chars <- c(chars, paste0("  ", normative_counts$medevac_status_label[i]))
  vals <- c(vals, sprintf("%d", normative_counts$n[i]))
}

# Add rest
chars <- c(chars, "",
           "**Physicians**",
           "  Total Physicians",
           "",
           "**Responses**",
           "  Total Responses",
           "",
           "**Years in Practice**",
           "  Median [IQR]",
           "  Mean (SD)",
           "  Range",
           "",
           "**Confidence (1-10 scale)**",
           "  Mean (SD)",
           "  Median [IQR]",
           "",
           "**Medevac Selection**",
           "  Overall % Choosing Medevac",
           "  Range Across Physicians")

vals <- c(vals, "",
          "",
          as.character(length(unique(data$physician_id))),
          "",
          "",
          as.character(nrow(data)),
          "",
          "",
          sprintf("%.0f [%.0f - %.0f]", 
                  median(physician_summary$years_experience),
                  quantile(physician_summary$years_experience, 0.25),
                  quantile(physician_summary$years_experience, 0.75)),
          sprintf("%.1f (%.1f)", mean(physician_summary$years_experience), 
                  sd(physician_summary$years_experience)),
          sprintf("%d - %d years", 
                  min(physician_summary$years_experience),
                  max(physician_summary$years_experience)),
          "",
          "",
          sprintf("%.1f (%.1f)", mean(data$confidence, na.rm = TRUE), 
                  sd(data$confidence, na.rm = TRUE)),
          sprintf("%.0f [%.0f - %.0f]", 
                  median(data$confidence, na.rm = TRUE),
                  quantile(data$confidence, 0.25, na.rm = TRUE),
                  quantile(data$confidence, 0.75, na.rm = TRUE)),
          "",
          "",
          sprintf("%.1f%%", 100 * mean(data$chose_medevac)),
          sprintf("%.1f%% - %.1f%%", 
                  min(physician_summary$pct_medevac),
                  max(physician_summary$pct_medevac)))

summary_stats <- data.frame(
  Characteristic = chars,
  Value = vals
)

kable(summary_stats,
      col.names = c("Characteristic", "Value"),
      caption = "Table 1: Sample Characteristics and Study Design",
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  )
```

---

# Figure 1: Response Distribution by Physician

```{r create-physician-letter-mapping}
# Create random letter assignment for physicians (A-Z)
# Set seed for reproducibility
set.seed(42)

# Get all unique physician IDs
all_physician_ids <- sort(unique(data$physician_id))

# Create random letter assignment (A-Z)
letters_available <- LETTERS[1:length(all_physician_ids)]
random_letters <- sample(letters_available, length(all_physician_ids), replace = FALSE)

# Create mapping dataframe
physician_letter_map <- data.frame(
  physician_id = all_physician_ids,
  physician_letter = random_letters,
  stringsAsFactors = FALSE
)
```

```{r figure1-physician-horizontal}
#| fig-height: 10
#| fig-width: 12

# Calculate proportion of each decision type for each physician
physician_decisions <- data %>%
  left_join(physician_letter_map, by = "physician_id") %>%
  group_by(physician_letter) %>%
  summarise(
    Medevac = sum(decision == "Medevac"),
    Commercial = sum(decision == "Commercial"),
    Remain = sum(decision == "Remain"),
    Total = n()
  ) %>%
  mutate(
    pct_medevac = 100 * Medevac / Total,
    pct_commercial = 100 * Commercial / Total,
    pct_remain = 100 * Remain / Total
  ) %>%
  arrange(desc(pct_medevac))

# Create long format for stacked bar
physician_long <- physician_decisions %>%
  select(Physician = physician_letter, Medevac = pct_medevac, 
         Commercial = pct_commercial, Remain = pct_remain) %>%
  pivot_longer(cols = c(Medevac, Commercial, Remain), 
               names_to = "Decision", values_to = "Percentage")

# Ensure correct factor ordering for stacking
physician_long$Decision <- factor(physician_long$Decision,
                                  levels = c("Remain", "Commercial", "Medevac"))

# Reorder physicians by total medevac percentage
physician_order <- physician_decisions %>%
  arrange(pct_medevac) %>%
  pull(physician_letter)

physician_long$Physician <- factor(physician_long$Physician, levels = physician_order)

# Create horizontal stacked bar chart
ggplot(physician_long, aes(x = Physician, y = Percentage, fill = Decision)) +
  geom_col(position = "stack", width = 0.8) +
  coord_flip() +
  scale_fill_manual(
    values = c("Medevac" = "#E74C3C", "Commercial" = "#3498DB", "Remain" = "#2ECC71"),
    name = "Decision",
    breaks = c("Medevac", "Commercial", "Remain"),
    labels = c("Medevac", "Commercial", "Remain")
  ) +
  labs(
    title = "Figure 1: Response Distribution by Physician",
    y = "Proportion of Responses (%)",
    x = "Physician",
    fill = "Decision"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 25)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 9),
    legend.position = "bottom",
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  )
```

---

# Table 2: Descriptive Statistics by Vignette

```{r table2-combined}
# Use medevac_status_label directly (matches Table 1 classification)
vignette_desc <- data %>%
  group_by(question, medevac_status_label, question_type, vignette_class) %>%
  summarise(
    n = n(),
    pct_medevac = 100 * sum(decision == "Medevac") / n,
    pct_commercial = 100 * sum(decision == "Commercial") / n,
    pct_remain = 100 * sum(decision == "Remain") / n,
    mean_confidence = mean(confidence, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    # Create subclass names from original final_report
    # Reclassify D as B first
    vignette_class = ifelse(vignette_class == "D", "B", vignette_class),
    vignette_type = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac Only",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial Only",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain Only",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ as.character(question_type)
    ),
    # Find modal decision
    modal_decision = case_when(
      pct_medevac >= pct_commercial & pct_medevac >= pct_remain ~ "Medevac",
      pct_commercial >= pct_medevac & pct_commercial >= pct_remain ~ "Commercial",
      TRUE ~ "Remain"
    ),
    # Calculate agreement percentage (% choosing modal)
    agreement_pct = case_when(
      modal_decision == "Medevac" ~ pct_medevac,
      modal_decision == "Commercial" ~ pct_commercial,
      modal_decision == "Remain" ~ pct_remain
    )
  )

# Calculate Gwet's AC1 for each vignette (FIXED - using approach from final_report)
# Create wide format: one row per vignette, one column per physician
ratings_wide <- data %>%
  select(question, physician_id, decision) %>%
  pivot_wider(
    id_cols = question,
    names_from = physician_id,
    values_from = decision,
    names_prefix = "Physician_"
  )

ac1_by_vignette <- data %>%
  group_by(question) %>%
  summarise(
    decisions_vec = list(decision[!is.na(decision)]),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    decisions_vec = list(unlist(decisions_vec)),
    n_decisions = length(decisions_vec),
    n_unique = length(unique(decisions_vec)),
    
    gwet_ac1 = {
      if (n_decisions == 0 || n_unique <= 1) {
        if (n_decisions > 0 && n_unique == 1) {
          1.0  # Perfect agreement
        } else {
          NA_real_  # Cannot compute
        }
      } else {
        # Convert to numeric codes (1=Medevac, 2=Commercial, 3=Remain)
        decision_codes <- as.numeric(factor(decisions_vec, levels = c("Medevac", "Commercial", "Remain")))
        
        # Create ratings matrix: 1 row (one vignette), multiple columns (raters/physicians)
        ratings_matrix <- matrix(decision_codes, nrow = 1)
        
        # Calculate Gwet's AC1
        ac1_result <- tryCatch({
          result <- gwet.ac1.raw(ratings_matrix)
          round(result$est$coeff.val, 3)
        }, error = function(e) {
          NA_real_
        })
        ac1_result
      }
    },
    
    ac1_interpretation = case_when(
      is.na(gwet_ac1) && n_decisions == 0 ~ "Cannot compute",
      !is.na(gwet_ac1) && gwet_ac1 == 1.0 ~ "Perfect",
      is.na(gwet_ac1) ~ "Cannot compute",
      gwet_ac1 < 0.00 ~ "None",
      gwet_ac1 <= 0.20 ~ "Slight",
      gwet_ac1 <= 0.40 ~ "Fair",
      gwet_ac1 <= 0.60 ~ "Moderate",
      gwet_ac1 <= 0.80 ~ "Good",
      gwet_ac1 <= 0.99 ~ "Very Good",
      TRUE ~ "Perfect"
    )
  ) %>%
  ungroup() %>%
  select(question, gwet_ac1, ac1_interpretation)

# Join AC1 results to vignette_desc
vignette_desc <- vignette_desc %>%
  left_join(ac1_by_vignette, by = "question")

# Create display table
table2_display <- vignette_desc %>%
  select(
    `Vignette Type` = vignette_type,
    `Q#` = question,
    `Medevac %` = pct_medevac,
    `Commercial %` = pct_commercial,
    `Remain %` = pct_remain,
    `Modal` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    `Mean Conf.` = mean_confidence,
    # Keep medevac_status_label for grouping
    medevac_status = medevac_status_label
  )

kable(table2_display %>% select(-medevac_status),
      caption = "Table 2: Descriptive Statistics by Vignette",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(7, bold = TRUE,
              color = ifelse(table2_display$`Agreement %` >= 75, "darkgreen",
                           ifelse(table2_display$`Agreement %` >= 50, "orange", "red"))) %>%
  pack_rows("Medevac Only Wrong", 
            min(which(table2_display$medevac_status == "Medevac Only Wrong")),
            max(which(table2_display$medevac_status == "Medevac Only Wrong"))) %>%
  pack_rows("Medevac One of Two Wrong", 
            min(which(table2_display$medevac_status == "Medevac One of Two Wrong")),
            max(which(table2_display$medevac_status == "Medevac One of Two Wrong"))) %>%
  pack_rows("Ambiguous (All Plausible)", 
            min(which(table2_display$medevac_status == "Ambiguous (All Plausible)")),
            max(which(table2_display$medevac_status == "Ambiguous (All Plausible)"))) %>%
  pack_rows("Medevac One of Two Correct", 
            min(which(table2_display$medevac_status == "Medevac One of Two Correct")),
            max(which(table2_display$medevac_status == "Medevac One of Two Correct"))) %>%
  pack_rows("Medevac Only Correct", 
            min(which(table2_display$medevac_status == "Medevac Only Correct")),
            max(which(table2_display$medevac_status == "Medevac Only Correct")))
```

**Table 2 Notes:**
- **Gwet's AC1**: Chance-corrected agreement statistic (robust to prevalence)
- **Mean Conf.**: Average confidence rating (1-10 scale)
- Vignettes grouped by vignette type (matching Table 1 classification)

---

# Primary Analysis

## Mixed-Effects Model: Vignette Type + Confidence + Experience

```{r model-primary}
# Check correlation between experience and confidence
cor_exp_conf <- cor(data$years_experience, data$confidence, use = "complete.obs")

# Primary model: vignette type + confidence + experience (both centered, no interaction)
model_primary <- glmer(chose_medevac ~ medevac_status_label + 
                  confidence_centered +
                  years_experience_centered +
                  (1 | physician_id) + (1 | question),
                data = data,
                family = binomial(link = "logit"),
                control = glmerControl(optimizer = "bobyqa"))

# Extract variance components
vc <- as.data.frame(VarCorr(model_primary))
var_physician <- vc$vcov[vc$grp == "physician_id"]
var_vignette <- vc$vcov[vc$grp == "question"]
var_residual <- pi^2 / 3  # Logistic distribution residual variance
total_var <- var_physician + var_vignette + var_residual
icc_physician <- var_physician / total_var
icc_vignette <- var_vignette / total_var
mor_physician <- exp(sqrt(2 * var_physician) * qnorm(0.75))

# Get fixed effects
fixed_effects <- fixef(model_primary)
se <- sqrt(diag(vcov(model_primary)))
or <- exp(fixed_effects)
or_lower <- exp(fixed_effects - 1.96 * se)
or_upper <- exp(fixed_effects + 1.96 * se)
```

**Note:** Experience and confidence are moderately correlated (r = `r sprintf("%.2f", cor_exp_conf)`), but both are included as mean-centered continuous predictors to capture their independent effects.

## Table 3: Model Results - All Fixed Effects

```{r table3-model-fixed}
fixed_table <- data.frame(
  Predictor = c(
    "**Vignette Type**",
    "  Medevac Only Wrong (reference)",
    "  Medevac One of Two Wrong",
    "  Ambiguous (All Plausible)",
    "  Medevac One of Two Correct",
    "  Medevac Only Correct",
    "",
    "**Decision Characteristics**",
    "  Confidence (per 1-point increase)",
    "  Years of Experience (per 1-year increase)"
  ),
  OR = c(NA, 1.00, or[2:5], NA, NA, or[6:7]),
  CI_lower = c(NA, NA, or_lower[2:5], NA, NA, or_lower[6:7]),
  CI_upper = c(NA, NA, or_upper[2:5], NA, NA, or_upper[6:7]),
  p_value = c("", "ref", 
              ifelse(abs(fixed_effects[2:5] / se[2:5]) > 1.96, "< 0.05", "> 0.05"),
              "", "", 
              ifelse(abs(fixed_effects[6:7] / se[6:7]) > 1.96, "< 0.05", "> 0.05"))
) %>%
  mutate(
    OR_display = case_when(
      Predictor %in% c("**Vignette Type**", "", "**Decision Characteristics**") ~ "",
      Predictor == "  Medevac Only Wrong (reference)" ~ "1.00",
      !is.na(OR) ~ sprintf("%.2f", OR),
      TRUE ~ ""
    ),
    CI_display = case_when(
      Predictor %in% c("**Vignette Type**", "", "**Decision Characteristics**") ~ "",
      Predictor == "  Medevac Only Wrong (reference)" ~ "ref",
      !is.na(CI_lower) & !is.na(CI_upper) ~ sprintf("(%.2f - %.2f)", CI_lower, CI_upper),
      TRUE ~ ""
    )
  )

kable(fixed_table %>% select(Predictor, OR_display, CI_display, p_value),
      col.names = c("Predictor", "Odds Ratio", "95% CI", "P-value"),
      caption = "Table 3: Model Fixed Effects (Vignette Type + Confidence + Experience)",
      align = c("l", "c", "c", "c"),
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  )
```

**Interpretation:**

- **Confidence**: OR = `r sprintf("%.2f", or[6])` per 1-point increase (`r ifelse(abs(fixed_effects[6] / se[6]) > 1.96, "significant", "not significant")`)
- **Experience**: OR = `r sprintf("%.2f", or[7])` per 1-year increase (`r ifelse(abs(fixed_effects[7] / se[7]) > 1.96, "significant", "not significant")`)

---

## Table 4: Model Results - Variance Components

```{r table4-model-random}
variance_table <- data.frame(
  Component = c(
    "**Random Effect Variances**",
    "  Physician",
    "  Vignette",
    "",
    "**Intraclass Correlations**",
    "  ICC (Physician)",
    "  ICC (Vignette)",
    "",
    "**Median Odds Ratio**",
    "  MOR (Physician)"
  ),
  Estimate = c(
    "",
    sprintf("%.3f", var_physician),
    sprintf("%.3f", var_vignette),
    "",
    "",
    sprintf("%.1f%%", icc_physician * 100),
    sprintf("%.1f%%", icc_vignette * 100),
    "",
    "",
    sprintf("%.2f", mor_physician)
  )
)

kable(variance_table,
      col.names = c("Component", "Estimate"),
      caption = "Table 4: Model Variance Components",
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  )
```

**Key Findings:**

- ICC (Physician) = `r sprintf("%.1f%%", icc_physician * 100)`: Proportion of variance attributable to physician differences
- MOR = `r sprintf("%.2f", mor_physician)`: Indicates substantial residual practice variation
- Even after accounting for vignette appropriateness, confidence, and experience, meaningful physician-level differences persist

---

# Figures

## Figure 2: Marginal Predicted Probabilities by Vignette Type

```{r figure2-marginal-probs}
#| fig-height: 6
#| fig-width: 10

# Calculate marginal predicted probabilities from primary model with standard errors
categories <- c("Medevac Only Wrong",
               "Medevac One of Two Wrong",
               "Ambiguous (All Plausible)",
               "Medevac One of Two Correct",
               "Medevac Only Correct")

# Get variance-covariance matrix
vcov_mat <- vcov(model_primary)

# Calculate predicted log-odds and standard errors for each category
pred_logodds <- c(
  fixed_effects[1],  # Reference
  fixed_effects[1] + fixed_effects[2],
  fixed_effects[1] + fixed_effects[3],
  fixed_effects[1] + fixed_effects[4],
  fixed_effects[1] + fixed_effects[5]
)

# Calculate standard errors using delta method
se_logodds <- c(
  sqrt(vcov_mat[1,1]),  # Reference: just intercept variance
  sqrt(vcov_mat[1,1] + vcov_mat[2,2] + 2*vcov_mat[1,2]),  # Intercept + coef2 + covariance
  sqrt(vcov_mat[1,1] + vcov_mat[3,3] + 2*vcov_mat[1,3]),
  sqrt(vcov_mat[1,1] + vcov_mat[4,4] + 2*vcov_mat[1,4]),
  sqrt(vcov_mat[1,1] + vcov_mat[5,5] + 2*vcov_mat[1,5])
)

# Calculate 95% CI on log-odds scale
logodds_lower <- pred_logodds - 1.96 * se_logodds
logodds_upper <- pred_logodds + 1.96 * se_logodds

# Transform to probability scale
marginal_plot_data <- data.frame(
  category = factor(categories, levels = categories),
  category_num = 1:5,  # For x-axis positioning
  predicted = plogis(pred_logodds),
  lower = plogis(logodds_lower),
  upper = plogis(logodds_upper)
)

ggplot(marginal_plot_data, aes(x = category_num, y = predicted)) +
  geom_line(color = "#3498DB", size = 1.5) +
  geom_point(color = "#3498DB", size = 4) +
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                width = 0.15, size = 1, color = "#2C3E50") +
  geom_text(aes(label = sprintf("%.1f%%", predicted * 100)),
            vjust = -1.5, size = 4, fontface = "bold") +
  labs(
    title = "Figure 2: Appropriateness Gradient in Medevac Selection",
    subtitle = "Model-estimated probability of choosing medevac by vignette type (with 95% CI)",
    x = "Vignette Type",
    y = "Predicted Probability of Choosing Medevac"
  ) +
  scale_x_continuous(breaks = 1:5, labels = categories) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    panel.grid.minor = element_blank()
  )
```

---

## Figure 3: Physician-Level Variation

```{r figure3-physician-caterpillar}
#| fig-height: 10
#| fig-width: 12

# Extract physician random effects from primary model
ranef_model <- ranef(model_primary, condVar = TRUE)
physician_re <- ranef_model$physician_id
physician_se <- sqrt(attr(physician_re, "postVar")[1, 1, ])

physician_predictions <- data.frame(
  physician_id = rownames(physician_re),
  re = physician_re[, 1],
  se = physician_se
) %>%
  mutate(
    logit_medevac = fixed_effects[1] + re,
    prob_medevac = plogis(logit_medevac),
    logit_lower = logit_medevac - 1.96 * se,
    logit_upper = logit_medevac + 1.96 * se,
    prob_lower = plogis(logit_lower),
    prob_upper = plogis(logit_upper)
  ) %>%
  arrange(prob_medevac) %>%
  mutate(rank = row_number())

# Dynamic y-axis
y_max <- max(physician_predictions$prob_upper) * 1.05
y_min <- max(0, min(physician_predictions$prob_lower) * 0.95)

ggplot(physician_predictions, aes(x = rank, y = prob_medevac)) +
  geom_hline(yintercept = plogis(fixed_effects[1]), 
             linetype = "dashed", color = "#E74C3C", size = 1) +
  geom_point(size = 3, color = "#2C3E50") +
  geom_errorbar(aes(ymin = prob_lower, ymax = prob_upper), 
                width = 0.3, alpha = 0.7, color = "#2C3E50") +
  annotate("text", x = max(physician_predictions$rank) * 0.85, 
           y = plogis(fixed_effects[1]) + (y_max - y_min) * 0.08,
           label = "Average physician", 
           color = "#E74C3C", size = 4, fontface = "italic") +
  labs(
    title = "Figure 3: Physician-Level Variation",
    subtitle = "Adjusted for vignette type, confidence, and experience",
    x = "Physician (ordered by adjusted medevac propensity)",
    y = "Adjusted Probability of Choosing Medevac"
  ) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(y_min, y_max)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

**Figure 3 Interpretation:** After accounting for vignette appropriateness, confidence, and experience, residual physician variation ranges from `r sprintf("%.1f%%", min(physician_predictions$prob_medevac) * 100)` to `r sprintf("%.1f%%", max(physician_predictions$prob_medevac) * 100)`. The MOR of `r sprintf("%.2f", mor_physician)` indicates factors beyond measured covariates contribute to practice variation.

---

## Figure 4: Appropriateness Calibration by Physician

```{r figure4-calibration}
#| fig-height: 10
#| fig-width: 12

# Extract physician random effects from primary model
ranef_model <- ranef(model_primary, condVar = TRUE)
physician_re <- ranef_model$physician_id

# Calculate physician predictions for anchor categories
physician_re_df <- data.frame(
  physician_id = rownames(physician_re),
  physician_re = physician_re[, 1]
)

medevac_only_correct_effect <- fixed_effects["medevac_status_labelMedevac Only Correct"]

physician_calibration <- physician_re_df %>%
  mutate(
    prob_wrong = plogis(fixed_effects[1] + physician_re),
    prob_correct = plogis(fixed_effects[1] + medevac_only_correct_effect + physician_re)
  )

# Merge with experience for coloring
physician_calibration <- physician_calibration %>%
  mutate(physician_id = as.integer(physician_id)) %>%
  left_join(physician_experience, by = "physician_id")

ggplot(physician_calibration, aes(x = prob_wrong, y = prob_correct, color = years_experience)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray50", size = 1) +
  geom_point(size = 4, alpha = 0.8) +
  geom_text(aes(label = physician_id), hjust = -0.2, vjust = -0.5, size = 3, show.legend = FALSE) +
  scale_color_gradient(low = "#3498DB", high = "#E74C3C", name = "Years\nExperience") +
  annotate("text", x = 0.15, y = 0.15,
           label = "No discrimination\n(diagonal)", 
           angle = 45, size = 4, fontface = "italic", color = "gray50") +
  annotate("text", x = 0.15, y = 0.85,
           label = "Good discrimination\n(above diagonal)", 
           size = 4, fontface = "bold", color = "#27AE60") +
  labs(
    title = "Figure 4: Physician Appropriateness Calibration",
    subtitle = "Medevac propensity when 'Only Wrong' vs. 'Only Correct' (colored by experience)",
    x = "Predicted Prob. When Medevac Only Wrong",
    y = "Predicted Prob. When Medevac Only Correct"
  ) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 10),
    legend.position = "right",
    panel.grid.minor = element_blank()
  )
```

**Figure 4 Interpretation:** Most physicians are above the diagonal (appropriate discrimination). Distance from diagonal reflects calibration strength. Color shows years of experience - examining whether more experienced physicians show stronger calibration.

---

# Key Findings

**1. Strong appropriateness gradient exists** (Table 3, Figure 2)
   - Odds of choosing medevac increase systematically with appropriateness
   - Strong evidence of appropriate clinical reasoning

**2. Confidence and experience effects**
   - **Confidence**: OR = `r sprintf("%.2f", or[6])` per 1-point increase
   - **Experience**: OR = `r sprintf("%.2f", or[7])` per year

**3. Substantial residual variation persists**
   - ICC (Physician) = `r sprintf("%.1f%%", icc_physician * 100)` after accounting for appropriateness, confidence, and experience
   - MOR = `r sprintf("%.2f", mor_physician)`
   - Meaningful physician differences persist beyond measured covariates

The calibration plot (Figure 4) provides an actionable tool for feedback: physicians can see whether they appropriately discriminate between different appropriateness scenarios.

## Methodological Strengths

- **Mixed-effects framework** accounts for clustering (physicians + vignettes)
- **Explicit appropriateness modeling** moves beyond raw agreement
- **Variance decomposition** quantifies sources of variation
- **Multiple metrics** (ICC, MOR) for clinical interpretability

## Implications

This analysis suggests that while physicians generally respond appropriately to clinical scenarios, substantial **calibrated practice variation** remains. Understanding this variation is key to:

1. **Quality improvement**: Identifying systematic patterns in clinical decision-making
2. **Education**: Targeting feedback to appropriateness calibration
3. **Policy**: Accounting for legitimate variation vs. unwarranted variation
