---
title: "Physician Medevac Propensity Analysis"
subtitle: "Comprehensive Analysis of Clinical Appropriateness and Practice Variation"
author: "Medevac Interrater Study Team"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    theme: cosmo
    fig-width: 12
    fig-height: 8
    self-contained: true
    code-fold: true
    echo: false
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    colorlinks: true
    fig-width: 12
    fig-height: 8
    keep-tex: false
    echo: false
    include-in-header:
      text: |
        \usepackage{xcolor}
        \definecolor{darkgreen}{RGB}{0,100,0}
        \definecolor{orange}{RGB}{255,165,0}
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 8
)

# Load libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(here)
library(lme4)
library(gridExtra)
library(irrCAC)

# Load raw survey data for affiliations
raw_data <- read.csv(here::here("data", "survey_results.csv"), 
                     stringsAsFactors = FALSE)

# Load main processed data
data <- read.csv(here::here("data", "processed", "survey_data_processed.csv"),
                 stringsAsFactors = FALSE)

# Load medevac normative mapping
medevac_mapping <- read.csv(here::here("data", "medevac_normative_mapping.csv"),
                             stringsAsFactors = FALSE)

# Load physician experience data
physician_experience <- read.csv(here::here("data", "physician_experience.csv"),
                                 stringsAsFactors = FALSE)

# Merge with main data
data <- data %>%
  left_join(medevac_mapping %>% select(question, medevac_normative_status, medevac_status_label),
            by = "question") %>%
  left_join(physician_experience %>% select(physician_id, years_experience),
            by = "physician_id")

# Create binary outcomes and centered predictors
data <- data %>%
  mutate(
    # Primary outcome: chose medevac vs. not
    chose_medevac = ifelse(decision == "Medevac", 1, 0),
    # Set factor levels with Never Medevac as reference
    medevac_status_label = factor(medevac_status_label,
                                   levels = c("Never Medevac",
                                            "Medevac One of Two Wrong",
                                            "Ambiguous (All Plausible)",
                                            "Medevac One of Two Correct",
                                            "Always Medevac")),
    # Center continuous predictors for interpretation
    confidence_centered = confidence - mean(confidence, na.rm = TRUE),
    years_experience_centered = years_experience - mean(years_experience, na.rm = TRUE)
  )
```

# Executive Summary

This report examines physician variation in medevac decision-making through the lens of **clinical appropriateness**, with explicit modeling of **confidence** and **years of experience**.

We categorize all 20 vignettes by **vignette type** (appropriateness of the medevac option):

- **Always Medevac** (n=4): Medevac is the single best answer
- **Medevac One of Two Correct** (n=5): Medevac is appropriate, along with one other option
- **Ambiguous (All Plausible)** (n=3): All three options are reasonable
- **Medevac One of Two Wrong** (n=4): Medevac is inappropriate; two other options are reasonable
- **Never Medevac** (n=4): Medevac is the single worst answer

**Statistical Model**: Binary mixed-effects logistic regression
- Outcome: Chose medevac vs. not
- Fixed effects: Vignette type + Confidence (centered) + Experience (centered)
- Random effects: Physician + Vignette
- No interaction terms (for simplicity)

**Key Findings:**

1. **Strong appropriateness gradient**
   - Odds of choosing medevac increase systematically from "Never Medevac" to "Always Medevac"
   - Strong evidence of appropriate clinical reasoning

2. **Confidence and experience effects**
   - Confidence significantly predicts medevac choice
   - Experience shows positive trend
   - Together explain meaningful physician variance

3. **Substantial residual variation persists**
   - Even after accounting for appropriateness, confidence, and experience
   - Suggests additional unmeasured factors influence decision-making

---

# Table 1: Sample Characteristics and Study Design

```{r table1-expanded}

# Vignette counts by vignette type
normative_counts <- data %>%
  distinct(question, medevac_status_label) %>%
  count(medevac_status_label) %>%
  arrange(factor(medevac_status_label, 
                 levels = c("Never Medevac", "Medevac One of Two Wrong",
                            "Ambiguous (All Plausible)", "Medevac One of Two Correct",
                            "Always Medevac")))

# Calculate agreement statistics by vignette
agreement_by_vignette <- data %>%
  group_by(question) %>%
  summarise(
    n = n(),
    pct_medevac = 100 * sum(decision == "Medevac") / n,
    pct_commercial = 100 * sum(decision == "Commercial") / n,
    pct_remain = 100 * sum(decision == "Remain") / n,
    .groups = "drop"
  ) %>%
  mutate(
    # Find modal decision
    modal_decision = case_when(
      pct_medevac >= pct_commercial & pct_medevac >= pct_remain ~ "Medevac",
      pct_commercial >= pct_medevac & pct_commercial >= pct_remain ~ "Commercial",
      TRUE ~ "Remain"
    ),
    # Calculate agreement percentage (% choosing modal)
    agreement_pct = case_when(
      modal_decision == "Medevac" ~ pct_medevac,
      modal_decision == "Commercial" ~ pct_commercial,
      modal_decision == "Remain" ~ pct_remain
    )
  )

# Categorize vignettes by agreement level
agreement_categories <- agreement_by_vignette %>%
  mutate(
    agreement_cat = case_when(
      agreement_pct == 100 ~ "100%",
      agreement_pct >= 75 ~ "75-99%",
      agreement_pct >= 50 ~ "50-74%",
      TRUE ~ "<50%"
    )
  ) %>%
  count(agreement_cat)

# Create physician summary statistics
physician_summary <- data %>%
  group_by(physician_id) %>%
  summarise(
    years_experience = first(years_experience),
    n_responses = n(),
    n_medevac = sum(decision == "Medevac"),
    pct_medevac = 100 * mean(decision == "Medevac")
  )

# Calculate correct responses to Always/Never Medevac vignettes
correct_responses <- data %>%
  mutate(
    correct_always = ifelse(medevac_status_label == "Always Medevac" & decision == "Medevac", 1, 0),
    correct_never = ifelse(medevac_status_label == "Never Medevac" & decision != "Medevac", 1, 0),
    n_always_vignettes = ifelse(medevac_status_label == "Always Medevac", 1, 0),
    n_never_vignettes = ifelse(medevac_status_label == "Never Medevac", 1, 0)
  ) %>%
  summarise(
    n_correct_always = sum(correct_always),
    n_always_total = sum(n_always_vignettes),
    pct_correct_always = 100 * n_correct_always / n_always_total,
    n_correct_never = sum(correct_never),
    n_never_total = sum(n_never_vignettes),
    pct_correct_never = 100 * n_correct_never / n_never_total
  )

# Build comprehensive table manually to avoid mismatch
# New order: Physicians, Years in Practice, Vignettes, Total Responses, Inter-Rater, Confidence
chars <- c(
  "**Physicians**",
  "  Total Physicians",
  "",
  "**Years in Practice**",
  "  Median [IQR]",
  "  Range",
  "",
  "**Vignettes**",
  "  Total Vignettes"
)

vals <- c(
  "",
  as.character(length(unique(data$physician_id))),
  "",
  "",
  sprintf("%.0f [%.0f - %.0f]", 
          median(physician_summary$years_experience),
          quantile(physician_summary$years_experience, 0.25),
          quantile(physician_summary$years_experience, 0.75)),
  sprintf("%d - %d years", 
          min(physician_summary$years_experience),
          max(physician_summary$years_experience)),
  "",
  "",
  as.character(length(unique(data$question)))
)

# Add vignette normative counts
for(i in 1:nrow(normative_counts)) {
  chars <- c(chars, paste0("  ", normative_counts$medevac_status_label[i]))
  vals <- c(vals, sprintf("%d", normative_counts$n[i]))
}

# Add rest
chars <- c(chars, "",
           "**Responses**",
           "  Total Responses",
           "  Correct Responses to Always Medevac",
           "  Correct Responses to Never Medevac",
           "",
           "**Inter-Rater Agreement by Vignette**",
           "  Median [IQR]",
           "  Range",
           "  100% Agreement",
           "  75-99% Agreement",
           "  50-74% Agreement",
           "  <50% Agreement",
           "",
           "**Confidence (1-10 scale)**",
           "  Median [IQR]",
           "  Range")

vals <- c(vals, "",
          "",
          as.character(nrow(data)),
          sprintf("%.1f%% (n=%d)", correct_responses$pct_correct_always, correct_responses$n_correct_always),
          sprintf("%.1f%% (n=%d)", correct_responses$pct_correct_never, correct_responses$n_correct_never),
          "",
          "",
          sprintf("%.1f%% [%.1f%% - %.1f%%]", 
                  median(agreement_by_vignette$agreement_pct),
                  quantile(agreement_by_vignette$agreement_pct, 0.25),
                  quantile(agreement_by_vignette$agreement_pct, 0.75)),
          sprintf("%.1f%% - %.1f%%", 
                  min(agreement_by_vignette$agreement_pct),
                  max(agreement_by_vignette$agreement_pct)),
          sprintf("%d vignettes", ifelse(any(agreement_categories$agreement_cat == "100%"), 
                                          agreement_categories$n[agreement_categories$agreement_cat == "100%"], 0)),
          sprintf("%d vignettes", ifelse(any(agreement_categories$agreement_cat == "75-99%"), 
                                          agreement_categories$n[agreement_categories$agreement_cat == "75-99%"], 0)),
          sprintf("%d vignettes", ifelse(any(agreement_categories$agreement_cat == "50-74%"), 
                                          agreement_categories$n[agreement_categories$agreement_cat == "50-74%"], 0)),
          sprintf("%d vignettes", ifelse(any(agreement_categories$agreement_cat == "<50%"), 
                                          agreement_categories$n[agreement_categories$agreement_cat == "<50%"], 0)),
          "",
          "",
          sprintf("%.0f [%.0f - %.0f]", 
                  median(data$confidence, na.rm = TRUE),
                  quantile(data$confidence, 0.25, na.rm = TRUE),
                  quantile(data$confidence, 0.75, na.rm = TRUE)),
          sprintf("%.0f - %.0f", 
                  min(data$confidence, na.rm = TRUE),
                  max(data$confidence, na.rm = TRUE)))

summary_stats <- data.frame(
  Characteristic = chars,
  Value = vals
)

kable(summary_stats,
      col.names = c("Characteristic", "Value"),
      caption = "Table 1: Sample Characteristics and Study Design",
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  )
```

---

# Figure 1: Response Distribution by Physician

```{r create-physician-letter-mapping}
# Create experience quartile-based labeling for physicians
# Get unique physicians with their experience
physician_exp <- data %>%
  distinct(physician_id, years_experience) %>%
  arrange(years_experience)

# Calculate experience quartiles
exp_quartiles <- quantile(physician_exp$years_experience, probs = c(0, 0.25, 0.5, 0.75, 1.0))

# Assign quartile labels and sequential numbers within each quartile
physician_letter_map <- physician_exp %>%
  mutate(
    quartile = cut(years_experience,
                   breaks = exp_quartiles,
                   labels = c("A", "B", "C", "D"),
                   include.lowest = TRUE)
  ) %>%
  group_by(quartile) %>%
  mutate(
    quartile_num = row_number(),
    physician_letter = paste0(quartile, quartile_num)
  ) %>%
  ungroup() %>%
  select(physician_id, physician_letter, quartile, years_experience)

# Store quartile ranges for legend
quartile_ranges <- data.frame(
  quartile = c("A", "B", "C", "D"),
  range_text = c(
    sprintf("A = %.0f-%.0f years", floor(exp_quartiles[1]), floor(exp_quartiles[2])),
    sprintf("B = %.0f-%.0f years", floor(exp_quartiles[2])+1, floor(exp_quartiles[3])),
    sprintf("C = %.0f-%.0f years", floor(exp_quartiles[3])+1, floor(exp_quartiles[4])),
    sprintf("D = %.0f+ years", floor(exp_quartiles[4])+1)
  )
)
legend_text <- paste(quartile_ranges$range_text, collapse = ", ")
```

```{r figure1-physician-horizontal}
#| fig-height: 10
#| fig-width: 12

# Calculate proportion of each decision type for each physician
physician_decisions <- data %>%
  left_join(physician_letter_map, by = "physician_id") %>%
  group_by(physician_letter) %>%
  summarise(
    Medevac = sum(decision == "Medevac"),
    Commercial = sum(decision == "Commercial"),
    Remain = sum(decision == "Remain"),
    Total = n()
  ) %>%
  mutate(
    pct_medevac = 100 * Medevac / Total,
    pct_commercial = 100 * Commercial / Total,
    pct_remain = 100 * Remain / Total
  ) %>%
  arrange(desc(pct_medevac))

# Create long format for stacked bar
physician_long <- physician_decisions %>%
  select(Physician = physician_letter, Medevac = pct_medevac, 
         Commercial = pct_commercial, Remain = pct_remain) %>%
  pivot_longer(cols = c(Medevac, Commercial, Remain), 
               names_to = "Decision", values_to = "Percentage")

# Ensure correct factor ordering for stacking
physician_long$Decision <- factor(physician_long$Decision,
                                  levels = c("Remain", "Commercial", "Medevac"))

# Reorder physicians by total medevac percentage
physician_order <- physician_decisions %>%
  arrange(pct_medevac) %>%
  pull(physician_letter)

physician_long$Physician <- factor(physician_long$Physician, levels = physician_order)

# Create horizontal stacked bar chart
ggplot(physician_long, aes(x = Physician, y = Percentage, fill = Decision)) +
  geom_col(position = "stack", width = 0.8) +
  coord_flip() +
  scale_fill_manual(
    values = c("Medevac" = "#E74C3C", "Commercial" = "#3498DB", "Remain" = "#2ECC71"),
    name = "Decision",
    breaks = c("Medevac", "Commercial", "Remain"),
    labels = c("Medevac", "Commercial", "Remain")
  ) +
  labs(
    title = "Figure 1: Response Distribution by Physician",
    y = "Proportion of Responses (%)",
    x = "Physician",
    fill = "Decision"
  ) +
  scale_y_continuous(labels = scales::percent_format(scale = 1),
                     limits = c(0, 100),
                     breaks = seq(0, 100, 25)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 9, face = "bold"),
    legend.position = "bottom",
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank(),
    plot.caption = element_text(size = 11, hjust = 0.5, face = "bold")
  ) +
  labs(caption = paste("Physician labels indicate experience quartile:", legend_text))
```

---

# Table 2: Descriptive Statistics by Vignette

```{r table2-combined}
# Use medevac_status_label directly (matches Table 1 classification)
vignette_desc <- data %>%
  group_by(question, medevac_status_label, question_type, vignette_class) %>%
  summarise(
    n = n(),
    n_medevac = sum(decision == "Medevac"),
    n_commercial = sum(decision == "Commercial"),
    n_remain = sum(decision == "Remain"),
    pct_medevac = 100 * n_medevac / n,
    pct_commercial = 100 * n_commercial / n,
    pct_remain = 100 * n_remain / n,
    median_confidence = median(confidence, na.rm = TRUE),
    q25_confidence = quantile(confidence, 0.25, na.rm = TRUE),
    q75_confidence = quantile(confidence, 0.75, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    # Create subclass names from original final_report
    # Reclassify D as B first
    vignette_class = ifelse(vignette_class == "D", "B", vignette_class),
    vignette_type = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac Only",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial Only",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain Only",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ as.character(question_type)
    ),
    # Find modal decision
    modal_decision = case_when(
      pct_medevac >= pct_commercial & pct_medevac >= pct_remain ~ "Medevac",
      pct_commercial >= pct_medevac & pct_commercial >= pct_remain ~ "Commercial",
      TRUE ~ "Remain"
    ),
    # Calculate agreement percentage (% choosing modal)
    agreement_pct = case_when(
      modal_decision == "Medevac" ~ pct_medevac,
      modal_decision == "Commercial" ~ pct_commercial,
      modal_decision == "Remain" ~ pct_remain
    ),
    # Format display strings
    medevac_display = sprintf("%.1f%% (n=%d)", pct_medevac, n_medevac),
    commercial_display = sprintf("%.1f%% (n=%d)", pct_commercial, n_commercial),
    remain_display = sprintf("%.1f%% (n=%d)", pct_remain, n_remain),
    conf_display = sprintf("%.0f [%.0f-%.0f]", median_confidence, q25_confidence, q75_confidence)
  )

# Calculate Gwet's AC1 for each vignette (FIXED - using approach from final_report)
# Create wide format: one row per vignette, one column per physician
ratings_wide <- data %>%
  select(question, physician_id, decision) %>%
  pivot_wider(
    id_cols = question,
    names_from = physician_id,
    values_from = decision,
    names_prefix = "Physician_"
  )

ac1_by_vignette <- data %>%
  group_by(question) %>%
  summarise(
    decisions_vec = list(decision[!is.na(decision)]),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    decisions_vec = list(unlist(decisions_vec)),
    n_decisions = length(decisions_vec),
    n_unique = length(unique(decisions_vec)),
    
    gwet_ac1 = {
      if (n_decisions == 0 || n_unique <= 1) {
        if (n_decisions > 0 && n_unique == 1) {
          1.0  # Perfect agreement
        } else {
          NA_real_  # Cannot compute
        }
      } else {
        # Convert to numeric codes (1=Medevac, 2=Commercial, 3=Remain)
        decision_codes <- as.numeric(factor(decisions_vec, levels = c("Medevac", "Commercial", "Remain")))
        
        # Create ratings matrix: 1 row (one vignette), multiple columns (raters/physicians)
        ratings_matrix <- matrix(decision_codes, nrow = 1)
        
        # Calculate Gwet's AC1
        ac1_result <- tryCatch({
          result <- gwet.ac1.raw(ratings_matrix)
          round(result$est$coeff.val, 3)
        }, error = function(e) {
          NA_real_
        })
        ac1_result
      }
    },
    
    ac1_interpretation = case_when(
      is.na(gwet_ac1) && n_decisions == 0 ~ "Cannot compute",
      !is.na(gwet_ac1) && gwet_ac1 == 1.0 ~ "Perfect",
      is.na(gwet_ac1) ~ "Cannot compute",
      gwet_ac1 < 0.00 ~ "None",
      gwet_ac1 <= 0.20 ~ "Slight",
      gwet_ac1 <= 0.40 ~ "Fair",
      gwet_ac1 <= 0.60 ~ "Moderate",
      gwet_ac1 <= 0.80 ~ "Good",
      gwet_ac1 <= 0.99 ~ "Very Good",
      TRUE ~ "Perfect"
    )
  ) %>%
  ungroup() %>%
  select(question, gwet_ac1, ac1_interpretation)

# Join AC1 results to vignette_desc
vignette_desc <- vignette_desc %>%
  left_join(ac1_by_vignette, by = "question")

# Create display table with proper ordering
table2_display <- vignette_desc %>%
  # Arrange by medevac_status_label to ensure proper grouping
  arrange(factor(medevac_status_label, 
                 levels = c("Never Medevac", "Medevac One of Two Wrong",
                           "Ambiguous (All Plausible)", "Medevac One of Two Correct",
                           "Always Medevac")),
          question) %>%
  select(
    `Vignette Type` = vignette_type,
    `Q#` = question,
    `Medevac` = medevac_display,
    `Commercial` = commercial_display,
    `Remain` = remain_display,
    `Modal` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    `Median Conf. [IQR]` = conf_display,
    # Keep medevac_status_label for grouping
    medevac_status = medevac_status_label
  )

# Calculate row indices for each group
row_groups <- table2_display %>%
  mutate(row_num = row_number()) %>%
  group_by(medevac_status) %>%
  summarise(
    start = min(row_num),
    end = max(row_num),
    .groups = "drop"
  )

# Create base table
table2_kable <- kable(table2_display %>% select(-medevac_status),
      caption = "Table 2: Descriptive Statistics by Vignette",
      align = c("l", "r", "l", "l", "l", "l", "r", "r", "l", "l")) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  ) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(7, bold = TRUE,
              color = ifelse(table2_display$`Agreement %` >= 75, "darkgreen",
                           ifelse(table2_display$`Agreement %` >= 50, "orange", "red")))

# Add pack_rows for each group
for (i in 1:nrow(row_groups)) {
  group_name <- as.character(row_groups$medevac_status[i])
  table2_kable <- table2_kable %>%
    pack_rows(group_name, row_groups$start[i], row_groups$end[i])
}

table2_kable
```

**Table 2 Notes:**
- **Gwet's AC1**: Chance-corrected agreement statistic chosen over Cohen's Kappa due to superior performance with class imbalance. AC1 is less affected by prevalence and marginal probability asymmetry, making it more appropriate when decision options have unequal base rates across vignettes
- **Median Conf. [IQR]**: Median confidence rating with interquartile range (1-10 scale)
- Vignettes grouped by vignette type (matching Table 1 classification)

---

# Figure 2: Appropriateness Gradient

```{r figure2-marginal-probs}
#| fig-height: 6
#| fig-width: 10

# This figure is computed from model results but shown here for visual flow
# Model is defined in the Primary Analysis section below

# We'll compute this after the model, but display it here
# Use a placeholder approach by computing inline

# Quick model for this figure (will be same as primary model below)
model_for_fig2 <- glmer(chose_medevac ~ medevac_status_label + 
                  confidence_centered +
                  years_experience_centered +
                  (1 | physician_id) + (1 | question),
                data = data,
                family = binomial(link = "logit"),
                control = glmerControl(optimizer = "bobyqa"))

# Get fixed effects
fixed_effects_fig2 <- fixef(model_for_fig2)
vcov_mat_fig2 <- vcov(model_for_fig2)

# Calculate marginal predicted probabilities with standard errors
categories <- c("Never Medevac",
               "Medevac One of Two Wrong",
               "Ambiguous (All Plausible)",
               "Medevac One of Two Correct",
               "Always Medevac")

# Calculate predicted log-odds and standard errors for each category
pred_logodds <- c(
  fixed_effects_fig2[1],  # Reference
  fixed_effects_fig2[1] + fixed_effects_fig2[2],
  fixed_effects_fig2[1] + fixed_effects_fig2[3],
  fixed_effects_fig2[1] + fixed_effects_fig2[4],
  fixed_effects_fig2[1] + fixed_effects_fig2[5]
)

# Calculate standard errors using delta method
se_logodds <- c(
  sqrt(vcov_mat_fig2[1,1]),
  sqrt(vcov_mat_fig2[1,1] + vcov_mat_fig2[2,2] + 2*vcov_mat_fig2[1,2]),
  sqrt(vcov_mat_fig2[1,1] + vcov_mat_fig2[3,3] + 2*vcov_mat_fig2[1,3]),
  sqrt(vcov_mat_fig2[1,1] + vcov_mat_fig2[4,4] + 2*vcov_mat_fig2[1,4]),
  sqrt(vcov_mat_fig2[1,1] + vcov_mat_fig2[5,5] + 2*vcov_mat_fig2[1,5])
)

# Calculate 95% CI on log-odds scale
logodds_lower <- pred_logodds - 1.96 * se_logodds
logodds_upper <- pred_logodds + 1.96 * se_logodds

# Transform to probability scale
marginal_plot_data <- data.frame(
  category = factor(categories, levels = categories),
  category_num = 1:5,
  predicted = plogis(pred_logodds),
  lower = plogis(logodds_lower),
  upper = plogis(logodds_upper)
)

ggplot(marginal_plot_data, aes(x = category_num, y = predicted)) +
  geom_line(color = "#3498DB", size = 1.5) +
  geom_point(color = "#3498DB", size = 4) +
  geom_errorbar(aes(ymin = lower, ymax = upper), 
                width = 0.15, size = 1, color = "#2C3E50") +
  geom_text(aes(label = sprintf("%.1f%%", predicted * 100)),
            vjust = -1.5, size = 4, fontface = "bold") +
  labs(
    title = "Figure 2: Appropriateness Gradient in Medevac Selection",
    subtitle = "Model-estimated probability of choosing medevac by vignette type (with 95% CI)",
    x = "Vignette Type",
    y = "Predicted Probability of Choosing Medevac"
  ) +
  scale_x_continuous(breaks = 1:5, labels = categories) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1.08), breaks = seq(0, 1, 0.2)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    panel.grid.minor = element_blank()
  )
```

---

# Primary Analysis

## Mixed-Effects Model: Vignette Type + Confidence + Experience

```{r model-primary}
# Check correlation between experience and confidence
cor_exp_conf <- cor(data$years_experience, data$confidence, use = "complete.obs")

# Primary model: vignette type + confidence + experience (both centered, no interaction)
model_primary <- glmer(chose_medevac ~ medevac_status_label + 
                  confidence_centered +
                  years_experience_centered +
                  (1 | physician_id) + (1 | question),
                data = data,
                family = binomial(link = "logit"),
                control = glmerControl(optimizer = "bobyqa"))

# Extract variance components
vc <- as.data.frame(VarCorr(model_primary))
var_physician <- vc$vcov[vc$grp == "physician_id"]
var_vignette <- vc$vcov[vc$grp == "question"]
var_residual <- pi^2 / 3  # Logistic distribution residual variance
total_var <- var_physician + var_vignette + var_residual
icc_physician <- var_physician / total_var
icc_vignette <- var_vignette / total_var
mor_physician <- exp(sqrt(2 * var_physician) * qnorm(0.75))

# Get fixed effects
fixed_effects <- fixef(model_primary)
se <- sqrt(diag(vcov(model_primary)))
or <- exp(fixed_effects)
or_lower <- exp(fixed_effects - 1.96 * se)
or_upper <- exp(fixed_effects + 1.96 * se)
```

**Note:** Experience and confidence are moderately correlated (r = `r sprintf("%.2f", cor_exp_conf)`), but both are included as mean-centered continuous predictors to capture their independent effects.

## Table 3: Model Results - All Fixed Effects

```{r table3-model-fixed}
# Calculate p-values
z_scores <- fixed_effects / se
p_values <- 2 * (1 - pnorm(abs(z_scores)))

fixed_table <- data.frame(
  Predictor = c(
    "**Vignette Type**",
    "  Never Medevac (reference)",
    "  Medevac One of Two Wrong",
    "  Ambiguous (All Plausible)",
    "  Medevac One of Two Correct",
    "  Always Medevac",
    "",
    "**Decision Characteristics**",
    "  Confidence (per 1-point increase)",
    "  Years of Experience (per 1-year increase)"
  ),
  OR = c(NA, 1.00, or[2:5], NA, NA, or[6:7]),
  CI_lower = c(NA, NA, or_lower[2:5], NA, NA, or_lower[6:7]),
  CI_upper = c(NA, NA, or_upper[2:5], NA, NA, or_upper[6:7]),
  p_value_raw = c(NA, NA, p_values[2:5], NA, NA, p_values[6:7])
) %>%
  mutate(
    OR_display = case_when(
      Predictor %in% c("**Vignette Type**", "", "**Decision Characteristics**") ~ "",
      Predictor == "  Never Medevac (reference)" ~ "1.00",
      !is.na(OR) ~ sprintf("%.2f", OR),
      TRUE ~ ""
    ),
    CI_display = case_when(
      Predictor %in% c("**Vignette Type**", "", "**Decision Characteristics**") ~ "",
      Predictor == "  Never Medevac (reference)" ~ "ref",
      !is.na(CI_lower) & !is.na(CI_upper) ~ sprintf("(%.2f - %.2f)", CI_lower, CI_upper),
      TRUE ~ ""
    ),
    p_display = case_when(
      Predictor %in% c("**Vignette Type**", "", "**Decision Characteristics**") ~ "",
      Predictor == "  Never Medevac (reference)" ~ "ref",
      is.na(p_value_raw) ~ "",
      p_value_raw < 0.001 ~ "<0.001*",
      p_value_raw < 0.05 ~ sprintf("%.3f*", p_value_raw),
      TRUE ~ sprintf("%.3f", p_value_raw)
    )
  )

kable(fixed_table %>% select(Predictor, OR_display, CI_display, p_display),
      col.names = c("Predictor", "Odds Ratio", "95% CI", "P-value"),
      caption = "Table 3: Model Fixed Effects (Vignette Type + Confidence + Experience)",
      align = c("l", "c", "c", "c"),
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  ) %>%
  footnote(general = "* indicates statistically significant (p < 0.05)",
           general_title = "",
           footnote_as_chunk = TRUE)
```

**Interpretation:**

- **Confidence**: OR = `r sprintf("%.2f", or[6])` per 1-point increase (p = `r ifelse(p_values[6] < 0.001, "<0.001", sprintf("%.3f", p_values[6]))`)
- **Experience**: OR = `r sprintf("%.2f", or[7])` per 1-year increase (p = `r ifelse(p_values[7] < 0.001, "<0.001", sprintf("%.3f", p_values[7]))`)

---

## Table 4: Model Results - Variance Components

```{r table4-model-random}
variance_table <- data.frame(
  Component = c(
    "**Random Effect Variances**",
    "  Physician",
    "  Vignette",
    "",
    "**Intraclass Correlations**",
    "  ICC (Physician)",
    "  ICC (Vignette)",
    "",
    "**Median Odds Ratio**",
    "  MOR (Physician)"
  ),
  Estimate = c(
    "",
    sprintf("%.3f", var_physician),
    sprintf("%.3f", var_vignette),
    "",
    "",
    sprintf("%.1f%%", icc_physician * 100),
    sprintf("%.1f%%", icc_vignette * 100),
    "",
    "",
    sprintf("%.2f", mor_physician)
  )
)

kable(variance_table,
      col.names = c("Component", "Estimate"),
      caption = "Table 4: Model Variance Components",
      escape = FALSE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left"
  )
```

**Key Findings:**

- **ICC (Physician)** = `r sprintf("%.1f%%", icc_physician * 100)`: Proportion of total variance attributable to physician differences
- **MOR (Median Odds Ratio)** = `r sprintf("%.2f", mor_physician)`: The median increase in odds of choosing medevac when comparing a randomly selected physician with higher propensity to one with lower propensity. An MOR of `r sprintf("%.2f", mor_physician)` means that if two identical patients saw two randomly selected physicians, the odds of receiving medevac would differ by a factor of `r sprintf("%.2f", mor_physician)` on average (50% of the time)
- Even after accounting for vignette appropriateness, confidence, and experience, meaningful physician-level differences persist

---

## Figure 3: Physician-Level Variation

```{r figure3-physician-caterpillar}
#| fig-height: 10
#| fig-width: 12

# Extract physician random effects from primary model
ranef_model <- ranef(model_primary, condVar = TRUE)
physician_re <- ranef_model$physician_id
physician_se <- sqrt(attr(physician_re, "postVar")[1, 1, ])

physician_predictions <- data.frame(
  physician_id = rownames(physician_re),
  re = physician_re[, 1],
  se = physician_se
) %>%
  mutate(
    logit_medevac = fixed_effects[1] + re,
    prob_medevac = plogis(logit_medevac),
    logit_lower = logit_medevac - 1.96 * se,
    logit_upper = logit_medevac + 1.96 * se,
    prob_lower = plogis(logit_lower),
    prob_upper = plogis(logit_upper)
  ) %>%
  arrange(prob_medevac) %>%
  mutate(rank = row_number())

# Dynamic y-axis
y_max <- max(physician_predictions$prob_upper) * 1.05
y_min <- max(0, min(physician_predictions$prob_lower) * 0.95)

ggplot(physician_predictions, aes(x = rank, y = prob_medevac)) +
  geom_hline(yintercept = plogis(fixed_effects[1]), 
             linetype = "dashed", color = "#E74C3C", size = 1) +
  geom_point(size = 3, color = "#2C3E50") +
  geom_errorbar(aes(ymin = prob_lower, ymax = prob_upper), 
                width = 0.3, alpha = 0.7, color = "#2C3E50") +
  annotate("text", x = max(physician_predictions$rank) * 0.85, 
           y = plogis(fixed_effects[1]) + (y_max - y_min) * 0.08,
           label = "Average physician", 
           color = "#E74C3C", size = 4, fontface = "italic") +
  labs(
    title = "Figure 3: Physician-Level Variation",
    subtitle = "Adjusted for vignette type, confidence, and experience",
    x = "Physician (ordered by adjusted medevac propensity)",
    y = "Adjusted Probability of Choosing Medevac"
  ) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(y_min, y_max)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 10),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

**Figure 3 Interpretation:** After accounting for vignette appropriateness, confidence, and experience, residual physician variation ranges from `r sprintf("%.1f%%", min(physician_predictions$prob_medevac) * 100)` to `r sprintf("%.1f%%", max(physician_predictions$prob_medevac) * 100)`. The MOR of `r sprintf("%.2f", mor_physician)` indicates factors beyond measured covariates contribute to practice variation.

---

## Figure 4: Appropriateness Calibration by Physician

```{r figure4-calibration}
#| fig-height: 10
#| fig-width: 12

# Extract physician random effects from primary model
ranef_model <- ranef(model_primary, condVar = TRUE)
physician_re <- ranef_model$physician_id

# Calculate physician predictions for anchor categories
physician_re_df <- data.frame(
  physician_id = rownames(physician_re),
  physician_re = physician_re[, 1]
)

always_medevac_effect <- fixed_effects["medevac_status_labelAlways Medevac"]

physician_calibration <- physician_re_df %>%
  mutate(
    prob_never = plogis(fixed_effects[1] + physician_re),
    prob_always = plogis(fixed_effects[1] + always_medevac_effect + physician_re)
  )

# Merge with experience for coloring
physician_calibration <- physician_calibration %>%
  mutate(physician_id = as.integer(physician_id)) %>%
  left_join(physician_experience, by = "physician_id")

ggplot(physician_calibration, aes(x = prob_never, y = prob_always, color = years_experience)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray50", size = 1) +
  geom_point(size = 4, alpha = 0.8) +
  geom_text(aes(label = physician_id), hjust = -0.2, vjust = -0.5, size = 3, show.legend = FALSE) +
  scale_color_gradient(low = "#3498DB", high = "#E74C3C", name = "Years\nExperience") +
  annotate("text", x = 0.15, y = 0.15,
           label = "No discrimination\n(diagonal)", 
           angle = 45, size = 4, fontface = "italic", color = "gray50") +
  annotate("text", x = 0.15, y = 0.85,
           label = "Good discrimination\n(above diagonal)", 
           size = 4, fontface = "bold", color = "#27AE60") +
  labs(
    title = "Figure 4: Physician Appropriateness Calibration",
    subtitle = "Medevac propensity when 'Never Medevac' vs. 'Always Medevac' (colored by experience)",
    x = "Predicted Prob. When Never Medevac",
    y = "Predicted Prob. When Always Medevac"
  ) +
  scale_x_continuous(labels = scales::percent_format(), limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 10),
    legend.position = "right",
    panel.grid.minor = element_blank()
  )
```

**Figure 4 Interpretation:** Most physicians are above the diagonal (appropriate discrimination). Distance from diagonal reflects calibration strength. Color shows years of experience - examining whether more experienced physicians show stronger calibration.

---

# Key Findings

**1. Strong appropriateness gradient exists** (Table 3, Figure 2)
   - Odds of choosing medevac increase systematically with appropriateness
   - Strong evidence of appropriate clinical reasoning

**2. Confidence and experience effects**
   - **Confidence**: OR = `r sprintf("%.2f", or[6])` per 1-point increase
   - **Experience**: OR = `r sprintf("%.2f", or[7])` per year

**3. Substantial residual variation persists**
   - ICC (Physician) = `r sprintf("%.1f%%", icc_physician * 100)` after accounting for appropriateness, confidence, and experience
   - MOR = `r sprintf("%.2f", mor_physician)`
   - Meaningful physician differences persist beyond measured covariates

The calibration plot (Figure 4) provides an actionable tool for feedback: physicians can see whether they appropriately discriminate between different appropriateness scenarios.

## Methodological Strengths

- **Mixed-effects framework** accounts for clustering (physicians + vignettes)
- **Explicit appropriateness modeling** moves beyond raw agreement
- **Variance decomposition** quantifies sources of variation
- **Multiple metrics** (ICC, MOR) for clinical interpretability

## Implications

This analysis suggests that while physicians generally respond appropriately to clinical scenarios, substantial **calibrated practice variation** remains. Understanding this variation is key to:

1. **Quality improvement**: Identifying systematic patterns in clinical decision-making
2. **Education**: Targeting feedback to appropriateness calibration
3. **Policy**: Accounting for legitimate variation vs. unwarranted variation
