---
title: "Medevac Interrater Reliability Study"
subtitle: "Final Report"
author: "Medevac Interrater Study Team"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    theme: cosmo
    fig-width: 10
    fig-height: 6
    self-contained: true
    code-fold: false
    echo: false
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    colorlinks: true
    fig-width: 10
    fig-height: 6
    keep-tex: false
    echo: false
    include-in-header:
      text: |
        \usepackage{xcolor}
        \definecolor{darkgreen}{RGB}{0,100,0}
        \definecolor{orange}{RGB}{255,165,0}
        \usepackage{pdflscape}
        \usepackage{rotating}
---

```{r setup}
#| include: false
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(here)
library(irrCAC)  # For Gwet's AC1

# Load raw survey data to get physician affiliations
raw_data <- read.csv(here::here("data", "survey_results.csv"), 
                     stringsAsFactors = FALSE)

# ============================================================================
# PREPROCESS: Clean up column names
# ============================================================================
# Trim long "Question XX: ..." columns to just "Question_XX"

col_names <- names(raw_data)

# Find columns that match "Question X:" or "Question XX:" pattern
question_cols <- grep("^Question\\.[0-9]+\\.", col_names)

# For each question column, rename it
for (i in question_cols) {
  old_name <- col_names[i]
  # Extract question number
  question_num <- sub("^Question\\.([0-9]+)\\..*$", "\\1", old_name)
  # Create new name
  new_name <- paste0("Question_", question_num)
  col_names[i] <- new_name
}

# Also handle confidence columns that follow questions
confidence_cols <- grep("How\\.confident\\.are\\.you", col_names)
for (i in seq_along(confidence_cols)) {
  col_names[confidence_cols[i]] <- paste0("Confidence_", i)
}

# Apply cleaned names
names(raw_data) <- col_names

# Load processed data
data <- read.csv(here::here("data", "processed", "survey_data_processed.csv"), 
                 stringsAsFactors = FALSE)

# Reclassify Class D as Class B
data <- data %>%
  mutate(vignette_class = ifelse(vignette_class == "D", "B", vignette_class))
```

# Study Overview

## Table 1: Study Composition

This table provides a comprehensive overview of the study design, organized into two sections: Vignettes and Respondents.

```{r study-overview}
# ============================================================================
# SECTION 1: VIGNETTE COUNTS BY CLASS AND SUBCLASS
# ============================================================================

# Get unique vignettes with their classifications
# Reclassify D as B with "Medevac or Remain" subclass
vignette_info <- data %>%
  distinct(question, vignette_label, question_type, vignette_class) %>%
  mutate(
    # Reclassify D as B
    vignette_class = ifelse(vignette_class == "D", "B", vignette_class),
    subclass = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ NA_character_
    )
  )

# Count vignettes and create section
vignette_section <- data.frame(
  Category = c(
    "Total Vignettes",
    "  Class A (One Correct Answer)",
    "    Medevac",
    "    Commercial",
    "    Remain",
    "  Class B (Two Reasonable Options)",
    "    Medevac or Commercial",
    "    Commercial or Remain",
    "    Medevac or Remain",
    "  Class C (Highly Ambiguous)",
    "    All Options Reasonable"
  ),
  Value = as.character(c(
    nrow(vignette_info),
    sum(vignette_info$vignette_class == "A"),
    sum(vignette_info$subclass == "Medevac", na.rm = TRUE),
    sum(vignette_info$subclass == "Commercial", na.rm = TRUE),
    sum(vignette_info$subclass == "Remain", na.rm = TRUE),
    sum(vignette_info$vignette_class == "B"),
    sum(vignette_info$subclass == "Medevac or Commercial", na.rm = TRUE),
    sum(vignette_info$subclass == "Commercial or Remain", na.rm = TRUE),
    sum(vignette_info$subclass == "Medevac or Remain", na.rm = TRUE),
    sum(vignette_info$vignette_class == "C"),
    sum(vignette_info$subclass == "All Options Reasonable", na.rm = TRUE)
  )),
  stringsAsFactors = FALSE
)

# ============================================================================
# SECTION 2: RESPONDENT INFORMATION
# ============================================================================

# Extract respondent data from raw survey
# This is a simpler approach that handles multiple survey versions

# Get unique physicians from processed data
physician_ids <- unique(data$physician_id)

# Create a function to extract affiliation for each physician
get_affiliation <- function(pid, raw_df) {
  # Find row for this physician
  row_idx <- which(raw_df[[1]] == pid)[1]
  if(length(row_idx) == 0 || is.na(row_idx)) return("Unknown")
  
  # Check all columns for affiliation markers
  row_data <- raw_df[row_idx, ]
  
  # Look for "Checked" in columns with affiliation names
  if(any(grepl("Maniilaq", names(row_data)) & row_data == "Checked", na.rm = TRUE)) {
    return("Maniilaq")
  } else if(any(grepl("YKHC", names(row_data)) & row_data == "Checked", na.rm = TRUE)) {
    return("YKHC")
  } else if(any(grepl("ANMC", names(row_data)) & row_data == "Checked", na.rm = TRUE)) {
    return("ANMC")
  } else if(any(grepl("work.*Other", names(row_data)) & row_data == "Checked", na.rm = TRUE)) {
    return("Other")
  }
  
  return("Unknown")
}

# Extract year completed training
year_col_idx <- which(grepl("year.*complete.*training", names(raw_data), ignore.case = TRUE))[1]

# Build respondent data
respondent_data <- data.frame(
  physician_id = physician_ids,
  stringsAsFactors = FALSE
) %>%
  rowwise() %>%
  mutate(
    affiliation = get_affiliation(physician_id, raw_data),
    year_completed = {
      row_idx <- which(raw_data[[1]] == physician_id)[1]
      if(length(row_idx) > 0 && !is.na(row_idx)) {
        as.numeric(as.character(raw_data[[row_idx, year_col_idx]]))
      } else {
        NA_real_
      }
    },
    years_since_completion = 2025 - year_completed
  ) %>%
  ungroup()

# Calculate summary statistics
n_respondents <- nrow(respondent_data)
mean_years <- round(mean(respondent_data$years_since_completion, na.rm = TRUE), 1)
sd_years <- round(sd(respondent_data$years_since_completion, na.rm = TRUE), 1)
median_years <- median(respondent_data$years_since_completion, na.rm = TRUE)
range_years <- range(respondent_data$years_since_completion, na.rm = TRUE)

# Count by affiliation
affiliation_counts <- respondent_data %>%
  count(affiliation) %>%
  arrange(desc(n))

# Create respondent section
respondent_section <- data.frame(
  Category = c(
    "Total Physicians",
    "  By Affiliation:",
    paste0("    ", affiliation_counts$affiliation),
    "",
    "  Years Since Training:",
    paste0("    Mean (SD)"),
    paste0("    Median"),
    paste0("    Range")
  ),
  Value = as.character(c(
    n_respondents,
    "",
    affiliation_counts$n,
    "",
    "",
    paste0(mean_years, " (", sd_years, ")"),
    median_years,
    paste0(range_years[1], "-", range_years[2])
  )),
  stringsAsFactors = FALSE
)

# ============================================================================
# SECTION 3: RESPONSE METRICS
# ============================================================================

# Calculate vignette-level metrics for the Responses section
vignette_metrics <- data %>%
  group_by(question) %>%
  summarise(
    modal_decision = names(sort(table(decision), decreasing = TRUE))[1],
    agreement_pct = round(100 * max(table(decision)) / n(), 1),
    entropy = {
      props <- prop.table(table(decision))
      -sum(props * log2(props + 1e-10))
    },
    mean_confidence = mean(confidence, na.rm = TRUE),
    .groups = "drop"
  )

# Calculate overall metrics
total_responses <- nrow(data)
mean_agreement <- round(mean(vignette_metrics$agreement_pct), 1)
median_agreement <- round(median(vignette_metrics$agreement_pct), 1)
min_agreement <- min(vignette_metrics$agreement_pct)
max_agreement <- max(vignette_metrics$agreement_pct)
mean_confidence_overall <- round(mean(data$confidence, na.rm = TRUE), 1)
mean_entropy <- round(mean(vignette_metrics$entropy), 3)
n_high_agreement <- sum(vignette_metrics$agreement_pct >= 75)
n_low_agreement <- sum(vignette_metrics$agreement_pct < 50)

# Create responses section (simplified to only Total Responses)
responses_section <- data.frame(
  Category = c("Total Responses"),
  Value = as.character(total_responses),
  stringsAsFactors = FALSE
)

# ============================================================================
# COMBINE ALL SECTIONS
# ============================================================================

# Add section headers
vignette_header <- data.frame(Category = "**VIGNETTES**", Value = "", stringsAsFactors = FALSE)
respondent_header <- data.frame(Category = "**RESPONDENTS**", Value = "", stringsAsFactors = FALSE)
responses_header <- data.frame(Category = "**RESPONSES**", Value = "", stringsAsFactors = FALSE)

overview_table <- bind_rows(
  vignette_header,
  vignette_section,
  data.frame(Category = "", Value = "", stringsAsFactors = FALSE),  # Blank row separator
  respondent_header,
  respondent_section,
  data.frame(Category = "", Value = "", stringsAsFactors = FALSE),  # Blank row separator
  responses_header,
  responses_section
)

# ============================================================================
# DISPLAY TABLE
# ============================================================================

kable(overview_table,
      col.names = c("", ""),
      align = c("l", "r"),
      caption = "Study Composition: Vignettes, Respondents, and Response Metrics") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("hold_position", "scale_down")
  ) %>%
  # Section headers
  row_spec(which(overview_table$Category == "**VIGNETTES**"), 
           bold = TRUE, font_size = 14, background = "#e8f4f8") %>%
  row_spec(which(overview_table$Category == "**RESPONDENTS**"), 
           bold = TRUE, font_size = 14, background = "#e8f4f8") %>%
  row_spec(which(overview_table$Category == "**RESPONSES**"), 
           bold = TRUE, font_size = 14, background = "#e8f4f8") %>%
  # Main category rows in Vignettes section
  row_spec(2, bold = TRUE) %>%  # Total Vignettes
  row_spec(3, bold = TRUE, italic = TRUE) %>%  # Class A
  row_spec(8, bold = TRUE, italic = TRUE) %>%  # Class B
  row_spec(12, bold = TRUE, italic = TRUE)  # Class C
```

**Note:** This table summarizes the complete study composition with `r nrow(vignette_info)` unique clinical vignettes evaluated by `r n_respondents` physicians (mean experience: `r mean_years` years since training completion), generating `r total_responses` total responses.

---

```{r create-physician-letter-mapping}
# Create random letter assignment for physicians (A-Z)
# Set seed for reproducibility
set.seed(42)

# Get all unique physician IDs
all_physician_ids <- sort(unique(data$physician_id))

# Create random letter assignment (A-Z)
# Assuming we have 20 physicians
letters_available <- LETTERS[1:length(all_physician_ids)]
random_letters <- sample(letters_available, length(all_physician_ids), replace = FALSE)

# Create mapping dataframe
physician_letter_map <- data.frame(
  physician_id = all_physician_ids,
  physician_letter = random_letters,
  stringsAsFactors = FALSE
)
```

## Figure 1: Response Distribution by Physician

```{r figure1-physician-response-distribution}
# Get physician years data to mark experienced physicians
year_col_idx <- which(grepl("year.*complete.*training", names(raw_data), ignore.case = TRUE))[1]

physician_years_all <- data.frame(
  physician_id = raw_data[[1]],
  year_completed = as.numeric(as.character(raw_data[[year_col_idx]])),
  stringsAsFactors = FALSE
) %>%
  mutate(
    current_year = 2025,
    years_since_completion = current_year - year_completed,
    experienced = !is.na(years_since_completion) & years_since_completion > 5
  )

# Calculate proportion of each decision type for each physician (all respondents)
physician_decisions_all <- data %>%
  group_by(physician_id) %>%
  summarise(
    total_responses = n(),
    n_medevac = sum(decision == "Medevac", na.rm = TRUE),
    n_commercial = sum(decision == "Commercial", na.rm = TRUE),
    n_remain = sum(decision == "Remain", na.rm = TRUE),
    pct_medevac = round(100 * n_medevac / total_responses, 1),
    pct_commercial = round(100 * n_commercial / total_responses, 1),
    pct_remain = round(100 * n_remain / total_responses, 1),
    .groups = "drop"
  ) %>%
  # Join with letter mapping and years data
  left_join(physician_letter_map, by = "physician_id") %>%
  left_join(physician_years_all %>% select(physician_id, experienced), by = "physician_id") %>%
  arrange(desc(pct_medevac)) %>%
  mutate(
    # Add dagger for experienced physicians (>5 years)
    physician_label = ifelse(experienced, 
                             paste0("Respondent ", physician_letter, "\u2020"),
                             paste0("Respondent ", physician_letter)),
    # Create ordered factor for physician letter, sorted by % Medevac (highest at top)
    # Reverse the levels so highest appears at top of y-axis
    Physician = factor(physician_label, 
                       levels = rev(physician_label))
  )

# Reshape for stacked bars
physician_long_all <- physician_decisions_all %>%
  select(Physician, pct_medevac, pct_commercial, pct_remain) %>%
  pivot_longer(cols = c(pct_medevac, pct_commercial, pct_remain),
               names_to = "Decision",
               values_to = "Percentage") %>%
  mutate(
    Decision = case_when(
      Decision == "pct_medevac" ~ "Medevac",
      Decision == "pct_commercial" ~ "Commercial",
      Decision == "pct_remain" ~ "Remain"
    ),
    # CRITICAL: For coord_flip(), reverse the factor order so Medevac ends up on LEFT
    Decision = factor(Decision, levels = c("Remain", "Commercial", "Medevac"))
  )

# Create stacked bar chart using coord_flip() for better control
ggplot(physician_long_all, aes(x = Physician, y = Percentage, fill = Decision)) +
  geom_col(position = "stack", width = 0.8) +
  coord_flip() +
  scale_fill_manual(
    values = c(
      "Medevac" = "#E74C3C",
      "Commercial" = "#3498DB",
      "Remain" = "#2ECC71"
    ),
    name = "Decision",
    breaks = c("Medevac", "Commercial", "Remain"),
    labels = c("Medevac", "Commercial", "Remain")
  ) +
  labs(
    title = "Figure 1: Response Distribution by Physician",
    y = "Proportion of Responses (%)",
    x = "Physician",
    fill = "Decision Type",
    caption = "\u2020 Indicates >5 years since training completion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 9, hjust = 0),
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 11, face = "bold"),
    legend.text = element_text(size = 10),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 20))
```

---

## Overall Results

Mean Agreement %: `r mean_agreement`%

Median Agreement %: `r median_agreement`%

Agreement Range: `r min_agreement`% - `r max_agreement`%

Mean Confidence: `r mean_confidence_overall`

Mean Entropy: `r mean_entropy`

Vignettes with >=75% Agreement: `r n_high_agreement`

Vignettes with <50% Agreement: `r n_low_agreement`

---

## Tables 2.1-2.3: Summary Statistics by Individual Vignette

These tables show detailed statistics for each vignette organized by class, with response distributions presented as percentage and count (% (n=)).

```{r vignette-summary}
# Calculate summary statistics for each vignette
vignette_summary <- data %>%
  group_by(question, vignette_label, question_type, vignette_class) %>%
  summarise(
    n_responses = n(),
    
    # Count and percentage for each decision
    n_medevac = sum(decision == "Medevac", na.rm = TRUE),
    n_commercial = sum(decision == "Commercial", na.rm = TRUE),
    n_remain = sum(decision == "Remain", na.rm = TRUE),
    
    pct_medevac = round(100 * n_medevac / n_responses, 1),
    pct_commercial = round(100 * n_commercial / n_responses, 1),
    pct_remain = round(100 * n_remain / n_responses, 1),
    
    # Modal decision and agreement
    modal_decision = names(sort(table(decision), decreasing = TRUE))[1],
    agreement_pct = round(100 * max(table(decision)) / n(), 1),
    
    # Entropy (measure of disagreement/uncertainty)
    entropy = {
      props <- prop.table(table(decision))
      -sum(props * log2(props + 1e-10))
    },
    
    # Mean confidence
    mean_confidence = round(mean(confidence, na.rm = TRUE), 1),
    
    .groups = "drop"
  ) %>%
  mutate(
    # Create formatted strings: "% (n=X)"
    Medevac = sprintf("%.1f%% (n=%d)", pct_medevac, n_medevac),
    Commercial = sprintf("%.1f%% (n=%d)", pct_commercial, n_commercial),
    Remain = sprintf("%.1f%% (n=%d)", pct_remain, n_remain),
    
    # Add subclass classification
    subclass = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ as.character(vignette_class)
    ),
    
    # Calculate "Selected Valid Option %" for Class B
    valid_option_pct = case_when(
      subclass == "Medevac or Commercial" ~ pct_medevac + pct_commercial,
      subclass == "Commercial or Remain" ~ pct_commercial + pct_remain,
      subclass == "Medevac or Remain" ~ pct_medevac + pct_remain,
      TRUE ~ NA_real_
    ),
    
    # Create ordered factor for sorting
    subclass_order = factor(subclass, 
                           levels = c("Medevac", "Commercial", "Remain",
                                    "Medevac or Commercial", "Commercial or Remain",
                                    "Medevac or Remain", "All Options Reasonable"))
  )

# Calculate Gwet's AC1 for each vignette
# Use three-option calculation for all classes (Medevac, Commercial, Remain)
ac1_by_vignette <- data %>%
  group_by(question) %>%
  summarise(
    # Get all physician decisions for this vignette
    decisions_vec = list(decision[!is.na(decision)]),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    decisions_vec = list(unlist(decisions_vec)),
    n_decisions = length(decisions_vec),
    n_unique = length(unique(decisions_vec)),
    
    # Calculate AC1 using three-option calculation for all classes
    gwet_ac1 = {
      if (n_decisions == 0 || n_unique <= 1) {
        if (n_decisions > 0 && n_unique == 1) {
          1.0  # Perfect agreement
        } else {
          NA_real_  # Cannot compute
        }
      } else {
        # For all classes, use three-option calculation
        # Convert to numeric codes (1=Medevac, 2=Commercial, 3=Remain)
        decision_codes <- as.numeric(factor(decisions_vec, levels = c("Medevac", "Commercial", "Remain")))
        
        # Create ratings matrix: 1 row (one vignette), multiple columns (raters/physicians)
        ratings_matrix <- matrix(decision_codes, nrow = 1)
        
        # Calculate Gwet's AC1
        ac1_result <- tryCatch({
          result <- gwet.ac1.raw(ratings_matrix)
          round(result$est$coeff.val, 3)
        }, error = function(e) {
          NA_real_
        })
        ac1_result
      }
    },
    
    # Determine interpretation
    ac1_interpretation = case_when(
      is.na(gwet_ac1) && n_decisions == 0 ~ "Cannot compute",
      !is.na(gwet_ac1) && gwet_ac1 == 1.0 ~ "Perfect",
      is.na(gwet_ac1) ~ "Cannot compute",
      gwet_ac1 < 0.00 ~ "None",
      gwet_ac1 <= 0.20 ~ "Slight",
      gwet_ac1 <= 0.40 ~ "Fair",
      gwet_ac1 <= 0.60 ~ "Moderate",
      gwet_ac1 <= 0.80 ~ "Good",
      gwet_ac1 <= 0.99 ~ "Very Good",
      TRUE ~ "Perfect"
    )
  ) %>%
  ungroup() %>%
  select(question, gwet_ac1, ac1_interpretation)

# Join AC1 results to vignette_summary
vignette_summary <- vignette_summary %>%
  left_join(ac1_by_vignette, by = "question")
```

```{r table2-1-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table2-1-display}
# Filter for Class A
table2_1 <- vignette_summary %>%
  filter(vignette_class == "A") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table2_1,
      caption = "Table 2.1: Class A - One Correct Answer",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table2_1$`Agreement %` >= 75, "darkgreen",
                           ifelse(table2_1$`Agreement %` >= 50, "orange", "red")))
```

```{r table2-1-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

```{r table2-2-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table2-2-display}
# Filter for Class B
table2_2 <- vignette_summary %>%
  filter(vignette_class == "B") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table2_2,
      caption = "Table 2.2: Class B - Two Reasonable Options",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table2_2$`Agreement %` >= 75, "darkgreen",
                           ifelse(table2_2$`Agreement %` >= 50, "orange", "red"))) %>%
  column_spec(8, width = "1.5cm") %>%
  column_spec(9, width = "2cm")
```

```{r table2-2-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

```{r table2-3-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table2-3-display}
# Filter for Class C
table2_3 <- vignette_summary %>%
  filter(vignette_class == "C") %>%
  arrange(question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table2_3,
      caption = "Table 2.3: Class C - Highly Ambiguous",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table2_3$`Agreement %` >= 75, "darkgreen",
                           ifelse(table2_3$`Agreement %` >= 50, "orange", "red")))
```

```{r table2-3-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

**Note:** Each vignette was evaluated by `r length(unique(data$physician_id))` physicians. Agreement % (highlighted in green ≥75%, orange 50-74%, red <50%) indicates the percentage who selected the modal decision. Entropy measures disagreement (0 = perfect agreement, higher = more disagreement).

---

## Figure 2: Agreement and Confidence by Subclass

```{r figure1-dual-axis}
# Calculate mean agreement % and confidence by subclass
subclass_metrics <- vignette_summary %>%
  group_by(vignette_class, subclass) %>%
  summarise(
    mean_agreement = mean(agreement_pct, na.rm = TRUE),
    mean_confidence = mean(mean_confidence, na.rm = TRUE),
    n_vignettes = n(),
    .groups = "drop"
  ) %>%
  mutate(
    # Create Class label for grouping
    Class = case_when(
      vignette_class == "A" ~ "Class A: One Correct Answer",
      vignette_class == "B" ~ "Class B: Two Reasonable Options",
      vignette_class == "C" ~ "Class C: Highly Ambiguous",
      TRUE ~ vignette_class
    ),
    # Order subclasses within each class
    subclass_order = factor(subclass, 
                            levels = c("Medevac", "Commercial", "Remain",
                                     "Medevac or Commercial", "Commercial or Remain",
                                     "Medevac or Remain", "All Options Reasonable"))
  ) %>%
  arrange(vignette_class, subclass_order) %>%
  mutate(
    subclass_factor = factor(subclass, 
                              levels = unique(subclass[order(vignette_class, subclass_order)]))
  )

# Reshape data for side-by-side bars
subclass_long <- subclass_metrics %>%
  select(subclass_factor, Class, mean_agreement, mean_confidence) %>%
  pivot_longer(cols = c(mean_agreement, mean_confidence),
               names_to = "Metric",
               values_to = "Value") %>%
  mutate(
    Metric = case_when(
      Metric == "mean_agreement" ~ "Agreement %",
      Metric == "mean_confidence" ~ "Confidence"
    ),
    # Scale confidence to 0-100 for comparison (will use secondary axis)
    Value_scaled = ifelse(Metric == "Confidence", Value * 10, Value),
    # Create fill variable that combines class and metric
    Fill = paste(Class, Metric, sep = "_")
  )

# Create the plot with side-by-side bars
ggplot(subclass_long, aes(x = subclass_factor, y = Value_scaled, fill = Fill)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(
    values = c(
      # Class A
      "Class A: One Correct Answer_Agreement %" = "#4A90E2",
      "Class A: One Correct Answer_Confidence" = "#87CEEB",
      # Class B
      "Class B: Two Reasonable Options_Agreement %" = "#50C878",
      "Class B: Two Reasonable Options_Confidence" = "#90EE90",
      # Class C
      "Class C: Highly Ambiguous_Agreement %" = "#FF6B6B",
      "Class C: Highly Ambiguous_Confidence" = "#FFB6C1"
    ),
    guide = "none"
  ) +
  scale_y_continuous(
    name = "Agreement %",
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    sec.axis = sec_axis(~ . / 10, name = "Mean Confidence (1-10)", breaks = seq(0, 10, 2))
  ) +
  labs(
    title = "Figure 2: Agreement and Confidence by Subclass",
    x = "Subclass (grouped by Class)",
    y = "Agreement %",
    caption = "Left axis: Agreement %. Right axis: Mean Confidence (1-10). Darker bars = Agreement %, Lighter bars = Confidence. Colors indicate Class."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.text.y.right = element_text(size = 10, color = "gray50"),
    axis.title = element_text(size = 12, face = "bold"),
    axis.title.y.right = element_text(color = "gray50"),
    plot.caption = element_text(size = 9, hjust = 0),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  geom_text(
    data = subclass_long,
    aes(
      label = ifelse(Metric == "Agreement %", 
                     paste0(round(Value, 1), "%"), 
                     paste0(round(Value, 1))),
      group = Fill,
      color = Metric
    ),
    position = position_dodge(width = 0.7),
    vjust = -0.5, 
    size = 3, 
    fontface = "bold"
  ) +
  scale_color_manual(
    values = c("Agreement %" = "black", "Confidence" = "gray50"),
    guide = "none"
  )
```

---

```{r calculate-n-high-conf}
# Calculate n for high confidence responses (used in header)
# Count unique physicians, not total responses
n_high_conf <- data %>% 
  filter(confidence >= 8) %>% 
  select(physician_id) %>% 
  distinct() %>% 
  nrow()
```

## Tables 3.1-3.3: Summary Statistics by Individual Vignette (High Confidence Only, n=`r n_high_conf`)

These tables show detailed statistics for each vignette, including only responses with confidence scores of 8 or higher.

```{r vignette-summary-high-confidence}
# Filter data to only include responses with confidence >= 8
data_high_conf <- data %>%
  filter(confidence >= 8)

# Calculate summary statistics for each vignette (high confidence only)
vignette_summary_high_conf <- data_high_conf %>%
  group_by(question, vignette_label, question_type, vignette_class) %>%
  summarise(
    n_responses = n(),
    
    # Count and percentage for each decision
    n_medevac = sum(decision == "Medevac", na.rm = TRUE),
    n_commercial = sum(decision == "Commercial", na.rm = TRUE),
    n_remain = sum(decision == "Remain", na.rm = TRUE),
    
    pct_medevac = round(100 * n_medevac / n_responses, 1),
    pct_commercial = round(100 * n_commercial / n_responses, 1),
    pct_remain = round(100 * n_remain / n_responses, 1),
    
    # Modal decision and agreement
    modal_decision = names(sort(table(decision), decreasing = TRUE))[1],
    agreement_pct = round(100 * max(table(decision)) / n(), 1),
    
    # Entropy (measure of disagreement/uncertainty)
    entropy = {
      props <- prop.table(table(decision))
      -sum(props * log2(props + 1e-10))
    },
    
    # Mean confidence
    mean_confidence = round(mean(confidence, na.rm = TRUE), 1),
    
    .groups = "drop"
  ) %>%
  mutate(
    # Create formatted strings: "% (n=X)"
    Medevac = sprintf("%.1f%% (n=%d)", pct_medevac, n_medevac),
    Commercial = sprintf("%.1f%% (n=%d)", pct_commercial, n_commercial),
    Remain = sprintf("%.1f%% (n=%d)", pct_remain, n_remain),
    
    # Add subclass classification
    subclass = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ as.character(vignette_class)
    ),
    
    # Create ordered factor for sorting
    subclass_order = factor(subclass, 
                           levels = c("Medevac", "Commercial", "Remain",
                                    "Medevac or Commercial", "Commercial or Remain",
                                    "Medevac or Remain", "All Options Reasonable"))
  )

# Calculate Gwet's AC1 for high confidence responses
# Use three-option calculation for all classes (Medevac, Commercial, Remain)
ac1_by_vignette_high_conf <- data_high_conf %>%
  group_by(question) %>%
  summarise(
    decisions_vec = list(decision[!is.na(decision)]),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    decisions_vec = list(unlist(decisions_vec)),
    n_decisions = length(decisions_vec),
    n_unique = length(unique(decisions_vec)),
    
    gwet_ac1 = {
      if (n_decisions == 0 || n_unique <= 1) {
        if (n_decisions > 0 && n_unique == 1) {
          1.0
        } else {
          NA_real_
        }
      } else {
        # For all classes, use three-option calculation
        decision_codes <- as.numeric(factor(decisions_vec, levels = c("Medevac", "Commercial", "Remain")))
        ratings_matrix <- matrix(decision_codes, nrow = 1)
        ac1_result <- tryCatch({
          result <- gwet.ac1.raw(ratings_matrix)
          round(result$est$coeff.val, 3)
        }, error = function(e) {
          NA_real_
        })
        ac1_result
      }
    },
    
    ac1_interpretation = case_when(
      is.na(gwet_ac1) && n_decisions == 0 ~ "Cannot compute",
      !is.na(gwet_ac1) && gwet_ac1 == 1.0 ~ "Perfect",
      is.na(gwet_ac1) ~ "Cannot compute",
      gwet_ac1 < 0.00 ~ "None",
      gwet_ac1 <= 0.20 ~ "Slight",
      gwet_ac1 <= 0.40 ~ "Fair",
      gwet_ac1 <= 0.60 ~ "Moderate",
      gwet_ac1 <= 0.80 ~ "Good",
      gwet_ac1 <= 0.99 ~ "Very Good",
      TRUE ~ "Perfect"
    )
  ) %>%
  ungroup() %>%
  select(question, gwet_ac1, ac1_interpretation)

# Join AC1 results to vignette_summary_high_conf
vignette_summary_high_conf <- vignette_summary_high_conf %>%
  left_join(ac1_by_vignette_high_conf, by = "question")
```

### Table 3.1: One Correct Answer (High Confidence Only)

```{r table3-1-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table3-1-display}
# Filter for Class A
table3_1 <- vignette_summary_high_conf %>%
  filter(vignette_class == "A") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table3_1,
      caption = "Table 3.1: Class A - One Correct Answer (Confidence >= 8)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table3_1$`Agreement %` >= 75, "darkgreen",
                           ifelse(table3_1$`Agreement %` >= 50, "orange", "red")))
```

```{r table3-1-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

### Table 3.2: Two Reasonable Options (High Confidence Only)

```{r table3-2-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table3-2-display}
# Filter for Class B
table3_2 <- vignette_summary_high_conf %>%
  filter(vignette_class == "B") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table3_2,
      caption = "Table 3.2: Class B - Two Reasonable Options (Confidence >= 8)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table3_2$`Agreement %` >= 75, "darkgreen",
                           ifelse(table3_2$`Agreement %` >= 50, "orange", "red"))) %>%
  column_spec(8, width = "1.5cm") %>%
  column_spec(9, width = "2cm")
```

```{r table3-2-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

### Table 3.3: Highly Ambiguous (High Confidence Only)

```{r table3-3-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table3-3-display}
# Filter for Class C
table3_3 <- vignette_summary_high_conf %>%
  filter(vignette_class == "C") %>%
  arrange(question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table3_3,
      caption = "Table 3.3: Class C - Highly Ambiguous (Confidence >= 8)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table3_3$`Agreement %` >= 75, "darkgreen",
                           ifelse(table3_3$`Agreement %` >= 50, "orange", "red")))
```

```{r table3-3-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

## Figure 3: Agreement and Confidence by Subclass (High Confidence Only, n=`r n_high_conf`)

```{r figure2-high-confidence}
# Calculate mean agreement % and confidence by subclass (high confidence only)
subclass_metrics_high_conf <- vignette_summary_high_conf %>%
  group_by(vignette_class, subclass) %>%
  summarise(
    mean_agreement = mean(agreement_pct, na.rm = TRUE),
    mean_confidence = mean(mean_confidence, na.rm = TRUE),
    n_vignettes = n(),
    .groups = "drop"
  ) %>%
  mutate(
    # Create Class label for grouping
    Class = case_when(
      vignette_class == "A" ~ "Class A: One Correct Answer",
      vignette_class == "B" ~ "Class B: Two Reasonable Options",
      vignette_class == "C" ~ "Class C: Highly Ambiguous",
      TRUE ~ vignette_class
    ),
    # Order subclasses within each class
    subclass_order = factor(subclass, 
                            levels = c("Medevac", "Commercial", "Remain",
                                     "Medevac or Commercial", "Commercial or Remain",
                                     "Medevac or Remain", "All Options Reasonable"))
  ) %>%
  arrange(vignette_class, subclass_order) %>%
  mutate(
    subclass_factor = factor(subclass, 
                              levels = unique(subclass[order(vignette_class, subclass_order)]))
  )

# Reshape data for side-by-side bars
subclass_long_high_conf <- subclass_metrics_high_conf %>%
  select(subclass_factor, Class, mean_agreement, mean_confidence) %>%
  pivot_longer(cols = c(mean_agreement, mean_confidence),
               names_to = "Metric",
               values_to = "Value") %>%
  mutate(
    Metric = case_when(
      Metric == "mean_agreement" ~ "Agreement %",
      Metric == "mean_confidence" ~ "Confidence"
    ),
    # Scale confidence to 0-100 for comparison (will use secondary axis)
    Value_scaled = ifelse(Metric == "Confidence", Value * 10, Value),
    # Create fill variable that combines class and metric
    Fill = paste(Class, Metric, sep = "_")
  )

# Create the plot with side-by-side bars
ggplot(subclass_long_high_conf, aes(x = subclass_factor, y = Value_scaled, fill = Fill)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(
    values = c(
      # Class A
      "Class A: One Correct Answer_Agreement %" = "#4A90E2",
      "Class A: One Correct Answer_Confidence" = "#87CEEB",
      # Class B
      "Class B: Two Reasonable Options_Agreement %" = "#50C878",
      "Class B: Two Reasonable Options_Confidence" = "#90EE90",
      # Class C
      "Class C: Highly Ambiguous_Agreement %" = "#FF6B6B",
      "Class C: Highly Ambiguous_Confidence" = "#FFB6C1"
    ),
    guide = "none"
  ) +
  scale_y_continuous(
    name = "Agreement %",
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    sec.axis = sec_axis(~ . / 10, name = "Mean Confidence (1-10)", breaks = seq(0, 10, 2))
  ) +
  labs(
    title = paste0("Figure 3: Agreement and Confidence by Subclass (High Confidence Only, n=", n_high_conf, ")"),
    x = "Subclass (grouped by Class)",
    y = "Agreement %",
    caption = "Left axis: Agreement %. Right axis: Mean Confidence (1-10). Darker bars = Agreement %, Lighter bars = Confidence. Colors indicate Class. Only includes responses with confidence >= 8."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.text.y.right = element_text(size = 10, color = "gray50"),
    axis.title = element_text(size = 12, face = "bold"),
    axis.title.y.right = element_text(color = "gray50"),
    plot.caption = element_text(size = 9, hjust = 0),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  geom_text(
    data = subclass_long_high_conf,
    aes(
      label = ifelse(Metric == "Agreement %", 
                     paste0(round(Value, 1), "%"), 
                     paste0(round(Value, 1))),
      group = Fill,
      color = Metric
    ),
    position = position_dodge(width = 0.7),
    vjust = -0.5, 
    size = 3, 
    fontface = "bold"
  ) +
  scale_color_manual(
    values = c("Agreement %" = "black", "Confidence" = "gray50"),
    guide = "none"
  )
```

---

```{r calculate-n-experienced}
# Calculate n for experienced respondents (used in header)
# First, get physician years since completion from raw_data
# Find the year column using grep (same approach as in Table 1)
year_col_idx <- which(grepl("year.*complete.*training", names(raw_data), ignore.case = TRUE))[1]

# Get physician IDs and years since completion
physician_years_data <- data.frame(
  physician_id = raw_data[[1]],  # First column is physician ID
  year_completed = as.numeric(as.character(raw_data[[year_col_idx]])),
  stringsAsFactors = FALSE
) %>%
  mutate(
    current_year = 2025,  # Match the year used in Table 1
    years_since_completion = current_year - year_completed
  ) %>%
  filter(!is.na(years_since_completion), years_since_completion > 5)

physician_years <- physician_years_data$physician_id

# Count unique physicians (not total responses)
n_experienced <- length(physician_years)
```

## Tables 4.1-4.3: Summary Statistics by Individual Vignette (Experienced Respondents Only, n=`r n_experienced`)

These tables show detailed statistics for each vignette, including only responses from physicians with more than 5 years since training completion.

```{r vignette-summary-experienced}
# Filter data to only include responses from experienced physicians (>5 years)
# First, get physician IDs with >5 years experience
experienced_physicians <- respondent_data %>%
  filter(years_since_completion > 5) %>%
  pull(physician_id)

data_experienced <- data %>%
  filter(physician_id %in% experienced_physicians)

# Calculate summary statistics for each vignette (experienced only)
vignette_summary_experienced <- data_experienced %>%
  group_by(question, vignette_label, question_type, vignette_class) %>%
  summarise(
    n_responses = n(),
    
    # Count and percentage for each decision
    n_medevac = sum(decision == "Medevac", na.rm = TRUE),
    n_commercial = sum(decision == "Commercial", na.rm = TRUE),
    n_remain = sum(decision == "Remain", na.rm = TRUE),
    
    pct_medevac = round(100 * n_medevac / n_responses, 1),
    pct_commercial = round(100 * n_commercial / n_responses, 1),
    pct_remain = round(100 * n_remain / n_responses, 1),
    
    # Modal decision and agreement
    modal_decision = names(sort(table(decision), decreasing = TRUE))[1],
    agreement_pct = round(100 * max(table(decision)) / n(), 1),
    
    # Entropy (measure of disagreement/uncertainty)
    entropy = {
      props <- prop.table(table(decision))
      -sum(props * log2(props + 1e-10))
    },
    
    # Mean confidence
    mean_confidence = round(mean(confidence, na.rm = TRUE), 1),
    
    .groups = "drop"
  ) %>%
  mutate(
    # Create formatted strings: "% (n=X)"
    Medevac = sprintf("%.1f%% (n=%d)", pct_medevac, n_medevac),
    Commercial = sprintf("%.1f%% (n=%d)", pct_commercial, n_commercial),
    Remain = sprintf("%.1f%% (n=%d)", pct_remain, n_remain),
    
    # Add subclass classification
    subclass = case_when(
      vignette_class == "A" & question_type == "Clear Medevac" ~ "Medevac",
      vignette_class == "A" & question_type == "Clear Commercial" ~ "Commercial",
      vignette_class == "A" & question_type == "Clear Remain" ~ "Remain",
      vignette_class == "B" & question_type == "Clear Not Medevac" ~ "Commercial or Remain",
      vignette_class == "B" & question_type == "Clear Not Remain" ~ "Medevac or Commercial",
      vignette_class == "B" & grepl("Conflict", question_type) ~ "Medevac or Remain",
      vignette_class == "C" ~ "All Options Reasonable",
      TRUE ~ as.character(vignette_class)
    ),
    
    # Create ordered factor for sorting
    subclass_order = factor(subclass, 
                           levels = c("Medevac", "Commercial", "Remain",
                                    "Medevac or Commercial", "Commercial or Remain",
                                    "Medevac or Remain", "All Options Reasonable"))
  )

# Calculate Gwet's AC1 for experienced respondents
# Use three-option calculation for all classes (Medevac, Commercial, Remain)
ac1_by_vignette_experienced <- data_experienced %>%
  group_by(question) %>%
  summarise(
    decisions_vec = list(decision[!is.na(decision)]),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    decisions_vec = list(unlist(decisions_vec)),
    n_decisions = length(decisions_vec),
    n_unique = length(unique(decisions_vec)),
    
    gwet_ac1 = {
      if (n_decisions == 0 || n_unique <= 1) {
        if (n_decisions > 0 && n_unique == 1) {
          1.0
        } else {
          NA_real_
        }
      } else {
        # For all classes, use three-option calculation
        decision_codes <- as.numeric(factor(decisions_vec, levels = c("Medevac", "Commercial", "Remain")))
        ratings_matrix <- matrix(decision_codes, nrow = 1)
        ac1_result <- tryCatch({
          result <- gwet.ac1.raw(ratings_matrix)
          round(result$est$coeff.val, 3)
        }, error = function(e) {
          NA_real_
        })
        ac1_result
      }
    },
    
    ac1_interpretation = case_when(
      is.na(gwet_ac1) && n_decisions == 0 ~ "Cannot compute",
      !is.na(gwet_ac1) && gwet_ac1 == 1.0 ~ "Perfect",
      is.na(gwet_ac1) ~ "Cannot compute",
      gwet_ac1 < 0.00 ~ "None",
      gwet_ac1 <= 0.20 ~ "Slight",
      gwet_ac1 <= 0.40 ~ "Fair",
      gwet_ac1 <= 0.60 ~ "Moderate",
      gwet_ac1 <= 0.80 ~ "Good",
      gwet_ac1 <= 0.99 ~ "Very Good",
      TRUE ~ "Perfect"
    )
  ) %>%
  ungroup() %>%
  select(question, gwet_ac1, ac1_interpretation)

# Join AC1 results to vignette_summary_experienced
vignette_summary_experienced <- vignette_summary_experienced %>%
  left_join(ac1_by_vignette_experienced, by = "question")
```

### Table 4.1: One Correct Answer (Experienced Respondents Only)

```{r table4-1-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table4-1-display}
# Filter for Class A
table4_1 <- vignette_summary_experienced %>%
  filter(vignette_class == "A") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table4_1,
      caption = "Table 4.1: Class A - One Correct Answer (>5 Years Experience)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table4_1$`Agreement %` >= 75, "darkgreen",
                           ifelse(table4_1$`Agreement %` >= 50, "orange", "red")))
```

```{r table4-1-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

### Table 4.2: Two Reasonable Options (Experienced Respondents Only)

```{r table4-2-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table4-2-display}
# Filter for Class B
table4_2 <- vignette_summary_experienced %>%
  filter(vignette_class == "B") %>%
  arrange(subclass_order, question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table4_2,
      caption = "Table 4.2: Class B - Two Reasonable Options (>5 Years Experience)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table4_2$`Agreement %` >= 75, "darkgreen",
                           ifelse(table4_2$`Agreement %` >= 50, "orange", "red"))) %>%
  column_spec(8, width = "1.5cm") %>%
  column_spec(9, width = "2cm")
```

```{r table4-2-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

### Table 4.3: Highly Ambiguous (Experienced Respondents Only)

```{r table4-3-landscape-begin, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\begin{landscape}\n")
}
```

```{r table4-3-display}
# Filter for Class C
table4_3 <- vignette_summary_experienced %>%
  filter(vignette_class == "C") %>%
  arrange(question) %>%
  select(
    Subclass = subclass,
    `Question Number` = question,
    Medevac,
    Commercial,
    Remain,
    `Modal Decision` = modal_decision,
    `Agreement %` = agreement_pct,
    `Gwet's AC1` = gwet_ac1,
    Interpretation = ac1_interpretation,
    Entropy = entropy,
    `Mean Conf.` = mean_confidence
  )

kable(table4_3,
      caption = "Table 4.3: Class C - Highly Ambiguous (>5 Years Experience)",
      align = c("l", "r", "r", "r", "r", "l", "r", "r", "l", "r", "r"),
      digits = c(0, 0, 1, 1, 1, 0, 1, 3, 0, 3, 1)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    position = "left",
    latex_options = c("scale_down", "hold_position")
  ) %>%
  column_spec(1, bold = TRUE, width = "2.5cm") %>%
  column_spec(2, bold = TRUE, width = "1cm") %>%
  column_spec(3:5, width = "2.5cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, bold = TRUE, width = "1.5cm", 
              color = ifelse(table4_3$`Agreement %` >= 75, "darkgreen",
                           ifelse(table4_3$`Agreement %` >= 50, "orange", "red")))
```

```{r table4-3-landscape-end, results='asis'}
if (knitr::is_latex_output()) {
  cat("\\end{landscape}\n")
}
```

---

## Figure 4: Agreement and Confidence by Subclass (Experienced Respondents Only, n=`r n_experienced`)

```{r figure3-experienced}
# Calculate mean agreement % and confidence by subclass (experienced only)
subclass_metrics_experienced <- vignette_summary_experienced %>%
  group_by(vignette_class, subclass) %>%
  summarise(
    mean_agreement = mean(agreement_pct, na.rm = TRUE),
    mean_confidence = mean(mean_confidence, na.rm = TRUE),
    n_vignettes = n(),
    .groups = "drop"
  ) %>%
  mutate(
    # Create Class label for grouping
    Class = case_when(
      vignette_class == "A" ~ "Class A: One Correct Answer",
      vignette_class == "B" ~ "Class B: Two Reasonable Options",
      vignette_class == "C" ~ "Class C: Highly Ambiguous",
      TRUE ~ vignette_class
    ),
    # Order subclasses within each class
    subclass_order = factor(subclass, 
                            levels = c("Medevac", "Commercial", "Remain",
                                     "Medevac or Commercial", "Commercial or Remain",
                                     "Medevac or Remain", "All Options Reasonable"))
  ) %>%
  arrange(vignette_class, subclass_order) %>%
  mutate(
    subclass_factor = factor(subclass, 
                              levels = unique(subclass[order(vignette_class, subclass_order)]))
  )

# Reshape data for side-by-side bars
subclass_long_experienced <- subclass_metrics_experienced %>%
  select(subclass_factor, Class, mean_agreement, mean_confidence) %>%
  pivot_longer(cols = c(mean_agreement, mean_confidence),
               names_to = "Metric",
               values_to = "Value") %>%
  mutate(
    Metric = case_when(
      Metric == "mean_agreement" ~ "Agreement %",
      Metric == "mean_confidence" ~ "Confidence"
    ),
    # Scale confidence to 0-100 for comparison (will use secondary axis)
    Value_scaled = ifelse(Metric == "Confidence", Value * 10, Value),
    # Create fill variable that combines class and metric
    Fill = paste(Class, Metric, sep = "_")
  )

# Create the plot with side-by-side bars
ggplot(subclass_long_experienced, aes(x = subclass_factor, y = Value_scaled, fill = Fill)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(
    values = c(
      # Class A
      "Class A: One Correct Answer_Agreement %" = "#4A90E2",
      "Class A: One Correct Answer_Confidence" = "#87CEEB",
      # Class B
      "Class B: Two Reasonable Options_Agreement %" = "#50C878",
      "Class B: Two Reasonable Options_Confidence" = "#90EE90",
      # Class C
      "Class C: Highly Ambiguous_Agreement %" = "#FF6B6B",
      "Class C: Highly Ambiguous_Confidence" = "#FFB6C1"
    ),
    guide = "none"
  ) +
  scale_y_continuous(
    name = "Agreement %",
    limits = c(0, 100),
    breaks = seq(0, 100, 20),
    sec.axis = sec_axis(~ . / 10, name = "Mean Confidence (1-10)", breaks = seq(0, 10, 2))
  ) +
  labs(
    title = paste0("Figure 4: Agreement and Confidence by Subclass (Experienced Respondents Only, n=", n_experienced, ")"),
    x = "Subclass (grouped by Class)",
    y = "Agreement %",
    caption = "Left axis: Agreement %. Right axis: Mean Confidence (1-10). Darker bars = Agreement %, Lighter bars = Confidence. Colors indicate Class. Only includes responses from physicians with >5 years since training completion."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 10),
    axis.text.y.right = element_text(size = 10, color = "gray50"),
    axis.title = element_text(size = 12, face = "bold"),
    axis.title.y.right = element_text(color = "gray50"),
    plot.caption = element_text(size = 9, hjust = 0),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  geom_text(
    data = subclass_long_experienced,
    aes(
      label = ifelse(Metric == "Agreement %", 
                     paste0(round(Value, 1), "%"), 
                     paste0(round(Value, 1))),
      group = Fill,
      color = Metric
    ),
    position = position_dodge(width = 0.7),
    vjust = -0.5, 
    size = 3, 
    fontface = "bold"
  ) +
  scale_color_manual(
    values = c("Agreement %" = "black", "Confidence" = "gray50"),
    guide = "none"
  )
```


